---
title: "bases_extract"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(sf) 
library(tidyverse)
library(viridis)
library(rvest)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
library(lwgeom)
library(cowplot)
library(purrr)
library(purrrlyr)
library(tmap)
library(raster)
library(ncdf4)
library(ncdump)
library(lubridate)
library(flipTime) # devtools::install_github("Displayr/flipTime")
library(fuzzyjoin)
library(RNetCDF)
library(tidync)
library(furrr)
library(humidity)
library(HeatStress) #devtools::install_github("anacv/HeatStress")
library(weathermetrics)
library(wbgt)  #devtools::install_github("mdljts/wbgt")
library(easyNCDF)
library(devtools)
library(tabularaster) #devtools::install_github("hypertidy/tabularaster")

# devtools::install_github("hypertidy/silicate")
#.libPaths()
```


Compile hourly dataframes for all installations except Portsmouth and Pensacola.

Process through 3 sets of extracted NLDAS folders of .rds objects:
1. nldas_raster
2. nldas_raster_joint
3. nldas_raster_end 2019
 



## Load Military Installations, Ranges, and Training Areas (MIRTA) Dataset
Accessed from: https://catalog.data.gov/dataset/military-installations-ranges-and-training-areas
Metadata updated date: January 18, 2017
```{r load_shapefile}
#Ref: http://strimas.com/r/tidy-sf/
bases <- st_read("D:/heat/installations_ranges/MIRTA_Boundaries.shp") %>% 
  janitor::clean_names()



# create table of centroids

centroid_coords <-
  bases %>% 
    dplyr::filter(
      .$site_name %in% c(
      "Fort Benning GA", "Fort Bragg","Fort Campbell",
      "Fort Jackson", "Fort Polk", "Fort Hood",
      "Fort Stewart", "Fort Leonard Wood", "Fort Riley",
      "NTC and Fort Irwin", "Fort Bliss", "Fort Lewis",
      "Fort Sill", "Fort Huachuca", "Fort Carson", "Fort Gordon",
      "West Point Mil Reservation", "Fort Drum",
      "MCB Quantico", "MCRD San Diego", "Twentynine Palms Main Base",
      "MCB Camp Lejeune", "MCRD Beaufort Parris Island", "MCB Camp Pendleton",
      "Eglin AFB", "Lackland AFB", "Fort Sam Houston", "NAS Pensacola", "Naval Medical Center Portsmouth")
      )%>% 
    mutate(centroid = st_centroid(geometry)) %>% 
    dplyr::select(-c("component", "joint_base", "country", "oper_stat")) %>% 
  as_tibble()


centroid_coords

# write_rds(centroid_coords, path = ("D:/output/centroid_coords.rds"))



# centroid lat/lon warning messages remain even after transformation:
#  sf::st_transform(4326)  -- same results

```

# 1. nldas_raster "1st set"

 .rds object list

```{r extract_variable_names}


file_list1 <- list.files(path = "D:/nldas_raster", pattern = "^.*\\.rds",
                        full.names = TRUE) %>% 
  as_tibble()


nldas_list1 <- list.files(path = "D:/nldas_raster", pattern = "^.*\\.rds",
                        full.names = TRUE) %>%  
  lapply(., read_rds)




# Set date/time as list element name

date_time_names <- 
  paste0(
      file_list1$value %>%  stringr::str_sub(start = -17)
  ) %>% 
  str_sub(end = -5)
        
        
        
#date_time_names %>% as_tibble() %>% n_distinct()
#date_time_names %>% as_tibble() %>% janitor::get_dupes(value)


names(nldas_list1) <- date_time_names

# write_rds(nldas_list1, path = "D:/output/nldas_list1.rds")


## Extract NLDAS from list for each location

#nldas_list1 <-
 # read_rds("D:/output/nldas_list1.rds")

first_set_bases <- c(
      "Fort Benning GA", "Fort Bragg","Fort Campbell",
      "Fort Jackson", "Fort Polk", "Fort Hood",
      "Fort Stewart", "Fort Leonard Wood", "Fort Riley",
      "NTC and Fort Irwin", "Fort Bliss", "Fort Lewis",
      "Fort Sill", "Fort Huachuca", "Fort Carson", "Fort Gordon",
      "West Point Mil Reservation", "Fort Drum") %>% 
  stringr::str_replace_all(., " ", "_") %>%
  stringr::str_to_lower()

# Extract by location from list and create an NLDAS object for each.

for (i in seq_along(first_set_bases)) {

nldas_list1 %>% 
    lapply(function(x) x[i,]) %>% 
    bind_rows(., .id = "date_time") %>% 
  write_rds(., path = paste0("D:/output/",  first_set_bases[i], ".rds" ))
}  


# read_rds("D:/output/fort_bragg.rds")


```




# 2nd set ("joint")



```{r}

file_list2 <- list.files(path = "D:/nldas_raster_joint", pattern = "^.*\\.rds",
                        full.names = TRUE) %>% 
  as_tibble()


nldas_list2 <- list.files(path = "D:/nldas_raster_joint", pattern = "^.*\\.rds",
                        full.names = TRUE) %>%  
  lapply(., read_rds)




# Set date/time as list element name

date_time_names <- 
  paste0(
      file_list2$value %>%  stringr::str_sub(start = -17)
  ) %>% 
  str_sub(end = -5)
        
        
        
#date_time_names %>% as_tibble() %>% n_distinct()
#date_time_names %>% as_tibble() %>% janitor::get_dupes(value)


names(nldas_list2) <- date_time_names

# write_rds(nldas_list2, path = "D:/output2/nldas_list2.rds")


## Extract NLDAS from list for each location

#nldas_list1 <-
 # read_rds("D:/output/nldas_list1.rds")

second_set_bases <- c(
           "MCB Quantico", "MCRD San Diego", "Twentynine Palms Main Base",
           "MCB Camp Lejeune", "MCRD Beaufort Parris Island", "MCB Camp Pendleton",
           "Eglin AFB", "Lackland AFB", "Fort Sam Houston") %>% 
  stringr::str_replace_all(., " ", "_") %>%
  stringr::str_to_lower()
  

second_set_bases 


# Extract by location from list and create an NLDAS object for each.

for (i in seq_along(second_set_bases)) {

nldas_list2 %>% 
    lapply(function(x) x[i,]) %>% 
    bind_rows(., .id = "date_time") %>% 
  write_rds(., path = paste0("D:/output/",  second_set_bases[i], ".rds" ))
}  

```




# Set 3 (end 2019)




```{r}

file_list3 <- list.files(path = "D:/nldas_raster_end2019", pattern = "^.*\\.rds",
                        full.names = TRUE) %>% 
  as_tibble()


nldas_list3 <- list.files(path = "D:/nldas_raster_end2019", pattern = "^.*\\.rds",
                        full.names = TRUE) %>%  
  lapply(., read_rds)




# Set date/time as list element name

date_time_names <- 
  paste0(
      file_list3$value %>%  stringr::str_sub(start = -17)
  ) %>% 
  str_sub(end = -5)
        
        
        
#date_time_names %>% as_tibble() %>% n_distinct()
#date_time_names %>% as_tibble() %>% janitor::get_dupes(value)


names(nldas_list3) <- date_time_names

# write_rds(nldas_list3, path = "D:/output2/nldas_list3.rds")


## Extract NLDAS from list for each location

#nldas_list1 <-
 # read_rds("D:/output/nldas_list1.rds")

full_set_bases <- c(
      "Fort Benning GA", "Fort Bragg","Fort Campbell",
      "Fort Jackson", "Fort Polk", "Fort Hood",
      "Fort Stewart", "Fort Leonard Wood", "Fort Riley",
      "NTC and Fort Irwin", "Fort Bliss", "Fort Lewis",
      "Fort Sill", "Fort Carson", "Fort Gordon", "Fort Drum",
      "MCB Quantico", "MCRD San Diego", "Twentynine Palms Main Base",
      "MCB Camp Lejeune", "MCRD Beaufort Parris Island", "MCB Camp Pendleton",
      "Eglin AFB", "Lackland AFB", "Fort Sam Houston") %>% 
  stringr::str_replace_all(., " ", "_") %>%
  stringr::str_to_lower()
  

full_set_bases 


# Extract by location from list and create an NLDAS object for each.

for (i in seq_along(full_set_bases)) {

nldas_list3 %>% 
    lapply(function(x) x[i,]) %>% 
    bind_rows(., .id = "date_time") %>% 
  write_rds(., path = paste0("D:/output2019/",  full_set_bases[i], ".rds" ))
}  

```



# Assemble master dataframe from 3 sets plus complete Pens/Portsmouth

```{r}


# Create index to substitute installation name into 
# master  dataframe id

df_index1 <- 
  list.files("D:/output") %>%
    as_tibble() %>% 
    mutate(row_id = row_number(),
           value = stringr::str_replace(value, ".rds", ""))

# Master dataframe (wide format)

nldas_df1 <-
  list.files("D:/output", full.names = TRUE) %>%
    map_dfr(.x = ., .f = read_rds, .id = "id") %>%
  mutate(id = as.integer(id)) %>% 
  left_join(df_index1, by = c("id" = "row_id")) %>% 
  rename(installation = value) %>% 
  dplyr::select(-id)

nldas_df1





df_index2 <- 
  list.files("D:/output2019") %>%
    as_tibble() %>% 
    mutate(row_id = row_number(),
           value = stringr::str_replace(value, ".rds", ""))

# Master dataframe (wide format)

nldas_df2 <-
  list.files("D:/output2019", full.names = TRUE) %>%
    map_dfr(.x = ., .f = read_rds, .id = "id") %>%
  mutate(id = as.integer(id)) %>% 
  left_join(df_index2, by = c("id" = "row_id")) %>% 
  rename(installation = value) %>% 
  dplyr::select(-id)

nldas_df2



df_index3 <- 
  list.files("D:/base_nldas_rds") %>%
    as_tibble() %>% 
    mutate(row_id = row_number(),
           value = stringr::str_replace(value, ".rds", ""))

# Master dataframe (wide format)

nldas_df3 <-
  list.files("D:/base_nldas_rds", full.names = TRUE) %>%
    map_dfr(.x = ., .f = read_rds, .id = "id") %>%
  mutate(id = as.integer(id)) %>% 
  left_join(df_index3, by = c("id" = "row_id")) %>% 
  rename(installation = value) %>% 
  dplyr::select(-id)

nldas_df3




nldas_hourly_df <-
  nldas_df1 %>% 
    bind_rows(nldas_df2) %>% 
    bind_rows(nldas_df3)




# Add on Fort Knox df

nldas_hourly_df <-
  read_rds(file = "D:/data/nldas_hourly_df.rds") %>% 
    bind_rows(knox_df)

# write_rds(nldas_hourly_df, file = "D:/data/nldas_hourly_df.rds")

centroid_coords <-
  read_rds(file = "D:/data/centroid_coords.rds") %>% 
  bind_rows(knox_sfc)

write_rds(centroid_coords, file = "D:/data/centroid_coords.rds")
```



