---
title: "counterfactuals"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


These findings suggest that implementation of control measures based on HI, instead of, or in addition to WBGT may effectively reduce HSI morbidity at sites where HI and WBGT poorly correlate in upper heat categories. For example, if preventive measures were initiated at an HI of 103°F, the NWS “Danger” classification level, with a similar OR reduction effect to maximum WBGT, the OR would hypothetically peak at 2.18, relative to an HI of 91°F, rather than continue to increase beyond 6.0 at 116°F, for an estimated reduction of ___ HSI cases per year.   


## Histogram for cases by Mac Heat Index
```{r}

hi_max_hist <-
  cc_exposure_df %>% 
  filter(case == 1) %>% 
  ggplot(aes(x = heat_index_max)) +
    geom_histogram(binwidth = 1, boundary = 0) +
    geom_vline(xintercept = 103) +
    theme_bw()

hi_max_hist
```



```{r}

## Convenience function
get_hist <- function(p) {
    d <- ggplot_build(p)$data[[1]]
    data.frame(x = d$x, xmin = d$xmin, xmax = d$xmax, y = d$y, cumsum = cumsum(d$y))
}

get_hist(hi_max_hist)

```

