---
title: "data_import"
author: "SL"
date: "5/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(Hmisc)
library(janitor)
library(skimr)
library(zoo)
library(naniar)

# packrat::snapshot()
```

## Import data files

HSI Data: sas7bdat format
DMIS IS Data: Excel format
```{r}

persons <-
  haven::read_sas("./data/R200131_persons.sas7bdat") %>%
  haven::zap_formats() %>% 
  haven::zap_label() %>%
  dplyr::mutate_at(vars(-BMI), haven::zap_empty) %>%  # convert empty character strings into missing values
  janitor::clean_names()


encounters <-
  haven::read_sas("./data/R200131_encounters.sas7bdat") %>%
  haven::zap_formats() %>% 
  haven::zap_label() %>% # remove SAS labels
  dplyr::mutate_at(vars(-D_EVENT), haven::zap_empty) %>%  # convert empty character strings into missing values
  janitor::clean_names() %>% 
  unique()   # remove duplicate rows 

# inspect missing values
encounters %>% 
  naniar::vis_miss(warn_large_data = FALSE)  
  
dmisid <- readxl::read_excel("./data/DMISID_FY2019.xlsx") %>% 
  janitor::clean_names() %>% 
  dplyr::select(dmis_id, 
                facility_unit_id = unit_id_code,
                facility_type = facility_type_code_6_char_maximum,
                facility_name = dmis_facility_name_30_character_maximum,
                facility_installation = installation_name_35_character_maximum, 
                facility_state = facility_state_code,
                facility_city = facility_city_name_32_character_maximum,
                facility_zipcode = facility_5_digit_zip_code,
                facility_region = health_service_region,
                facility_branch = branch_of_service_authority_code)


# Dataset Summaries: General

Hmisc::describe(encounters)
Hmisc::describe(persons)
skimr::skim(dmisid)


## Plot all encounters by date and type
# 
# encounters %>%
#   group_by(d_event, source) %>% 
#   summarise(n = dplyr::n()) %>% 
#   ggplot(aes(x = d_event, y = n)) +
#     geom_point() +
#     geom_line() +
#     facet_wrap(~source)
# 
# # By Year-Month
# encounters %>% 
#   mutate(year_mon = zoo::as.yearmon(d_event)) %>% 
#   group_by(year_mon, source) %>% 
#   summarise(n = dplyr::n()) %>% 
#   ggplot(aes(x = year_mon, y = n, color = source)) +
#     geom_point() +
#     geom_line() 
# 
# # By Year
# encounters %>% 
#   mutate(year = lubridate::year(d_event)) %>% 
#   group_by(year, source) %>% 
#   summarise(n = dplyr::n()) %>% 
#   ggplot(aes(x = year, y = n, color = source)) +
#     geom_point() +
#     geom_line()   

```



## Clean Data

## Multiple Encounters

For individuals who meet the case definition:
• The incidence date is considered the date of the first hospitalization, outpatient medical encounter, or reportable medical event that includes a defining diagnosis of heat illness.
• An individual is considered an incident case only once per calendar year.
• For individuals with more than one heat illness diagnosis in a calendar year, heat stroke is prioritized over heat exhaustion.
• Medical encounters for each individual within a calendar year are prioritized: hospitalizations > reportable medical events > ambulatory visits.


```{r}
# Inspect multiple encounters per studyid
encounters %>% 
  group_by(studyid) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  summary(n)



encounters %>% 
  group_by(studyid) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  ggplot() +
    geom_bar(aes(x = n))


encounters %>% 
  group_by(studyid, source) %>% 
  count() %>% 
  arrange(desc(source, n)) %>% 
  ggplot(aes(x = n)) +
    geom_bar() +
      facet_wrap(~source)+
      scale_y_continuous(trans = 'log10')


encounters %>% 
  group_by(studyid) %>% 
  tally() %>%
  dplyr::select(n) %>% as_vector() %>% 
  quantile(0.90)

encounters %>% 
  group_by(studyid, source) %>% 
  tally() %>% 
  count(n)
```


## Classify by HSI category (stroke, exhaustion, other)

- For Inpatient and Outpatient, use DX1/DX2 codes
- For RME, need to use "dx1_name" - alphanumeric DX codes not used after 2013

```{r}

# Classify each encounter as heat stroke, heat exhaustion, or other

# Classify RMEs

  # Inspect RME classification names

encounters %>% 
  dplyr::filter(source %in% "RME") %>% 
  count(dx1_name)
  
# 1 HEAT DEHYDRATION               7098  : heat_exhaustion (associated with DX 9923)
# 2 Heat Exhaustion                2442  : heat_exhaustion
# 3 HEAT EXHAUSTION                 356  : heat_exhaustion
# 4 HEAT ILLNESS                    128  : other
# 5 HEAT ILLNESS, HEAT EXHAUSTION  3184  : heat_exhaustion
# 6 HEAT ILLNESS, HEAT INJURY      1236  : other
# 7 HEAT ILLNESS, HEAT STROKE      2466  : heat_stroke
# 8 Heat Stroke                     654  : heat_stroke
# 9 HEAT STROKE                      45  : heat_stroke



  # Inspect RME "other" - do pre-2013 observations include DX codes? 

encounters %>% 
  dplyr::filter(source %in% "RME", 
                dx1_name %in% c("HEAT ILLNESS", "HEAT ILLNESS, HEAT INJURY" )) %>%  # 1,364 of 17,609 obs
  count(dx1) #dx2 codes all NA

  
#   dx1       n
#   <chr> <int>
# 1 992       1
# 2 9929    466
# 3 NA      897

# No, all remain classified as "other"(although many likly should have been entered as heat stroke or heat exhaustion)



rme_diag <-
  encounters %>% 
  dplyr::filter(source %in% "RME") %>% 
  dplyr::mutate(hsi = dplyr::case_when(
       str_detect(dx1_name, regex("exhaustion|dehydration", ignore_case = T))
       ~ "heat_exhaustion",
       str_detect(dx1_name, regex("stroke", ignore_case = T))
       ~ "heat_stroke",
       TRUE ~ "other"))
    
rme_diag %>% 
    count(hsi)


# Classify Inpatient and Outpatient
  # Inspect classification codes
encounters %>% 
  dplyr::filter(!source %in% "RME") %>% 
  count(dx1) %>% 
  dplyr::arrange(desc(n))

encounters %>% 
  dplyr::filter(!source %in% "RME") %>% 
  count(dx2) %>% 
  dplyr::arrange(desc(n))


in_out_diag <-
  encounters %>% 
   dplyr::filter(!source %in% "RME") %>% 
   dplyr::mutate(hsi = dplyr::case_when(
     str_detect(dx1, "T670XX[A-Z]") | str_detect(dx1, "9920") |
     str_detect(dx2, "T670XX[A-Z]") | str_detect(dx2, "9920")
     ~ "heat_stroke",
     str_detect(dx1, "T67[3459]XX[A-Z]") | str_detect(dx1, "992[345]") |
     str_detect(dx2, "T67[3459]XX[A-Z]") | str_detect(dx2, "992[345]")
     ~ "heat_exhaustion",
        TRUE ~ "other")) 

## Inspect inpatient/outpatient clasifications

in_out_diag %>% 
  group_by(source, hsi) %>% 
    count(hsi)

# in_out_diag %>%
#   mutate(year = lubridate::year(d_event)) %>%
#   group_by(year, source) %>%
#   summarise(n = dplyr::n()) %>%
#   ggplot(aes(x = year, y = n, color = source)) +
#     geom_point() +
#     geom_line()
# 
# in_out_diag %>%
#   mutate(year = lubridate::year(d_event)) %>%
#   group_by(year, source, hsi) %>%
#   summarise(n = dplyr::n()) %>%
#   ggplot(aes(x = year, y = n, color = source)) +
#     geom_point() +
#     geom_line() +
#     facet_wrap(~hsi)



```

## Combine RME and In/out-patient HSI-classified datasets

```{r}

encounters_diag <-
  in_out_diag %>%   # 121,796 obs
    dplyr::bind_rows(rme_diag) #17,609 obs

encounters_diag # 139,405 obs

encounters_diag %>% 
  count(hsi)

encounters_diag %>% 
  dplyr::group_by(source) %>% 
  count(hsi)

encounters_diag %>% 
  dplyr::group_by(source, hsi, year = lubridate::year(d_event)) %>%
  count(source) 

# encounters_diag %>%
#   mutate(year = lubridate::year(d_event)) %>%
#   group_by(year, source) %>%
#   summarise(n = dplyr::n()) %>%
#   ggplot(aes(x = year, y = n, color = source)) +
#     geom_point() +
#     geom_line()
# 
# encounters_diag %>%
#   mutate(year = lubridate::year(d_event)) %>%
#   group_by(year, source, hsi) %>%
#   summarise(n = dplyr::n()) %>%
#   ggplot(aes(x = year, y = n, color = hsi)) +
#     geom_point() +
#     geom_line() +
#     facet_wrap(~source, ncol = 1)


```


## Apply case definitions

```{r}

# Apply case definition: 
#   considered an incident case only once per calendar year
#   heat stroke is prioritized over heat exhaustion
#   includes only heat stroke and heat exhaustion - will retain "other" in datasets at this stage


# Identify observations to remove: 
#   more than 1 observation per studyid-year
#   heat stroke > heat exhaustion
#   hospitalizations > reportable medical events > ambulatory visits




# Remove `heat_exhaustion` or `other` if `heat_stroke` in studyid/year stratum

clean_non_heat_stroke <-
  encounters_diag %>% 
    dplyr::mutate(year = lubridate::year(d_event)) %>% 
    janitor::get_dupes(studyid, year) %>% # extract sets of instances with > 1 obs per studyid per year
    group_by(studyid, year) %>% 
    dplyr::filter(any(hsi == "heat_stroke")) %>% # filter strata that include a heat stroke obs
    dplyr::filter(!hsi %in% "heat_stroke") %>% # filter all non- heat stroke obs
    dplyr::ungroup() %>% 
    dplyr::select(-dupe_count, -year)

clean_non_heat_stroke # obs to be removed


clean_df_step1 <-
    encounters_diag %>% 
      dplyr::setdiff(clean_non_heat_stroke)  # remove rows that appear in `clean_non_heat_stroke`

# Inspect

clean_df_step1 %>% 
  count(hsi)

clean_df_step1 %>% 
  dplyr::group_by(source) %>% 
  count(hsi)

# clean_df_step1 %>%
#   mutate(year = lubridate::year(d_event)) %>%
#   group_by(year, source) %>%
#   summarise(n = dplyr::n()) %>%
#   ggplot(aes(x = year, y = n, color = source)) +
#     geom_point() +
#     geom_line()



  
 # Prioritize Hospitalizations
 
clean_prioritize_hosp <-
  clean_df_step1 %>% 
      dplyr::mutate(year = lubridate::year(d_event)) %>% 
        janitor::get_dupes(studyid, year) %>% # extract sets of instances with > 1 obs per studyid per year
        group_by(studyid, year) %>% 
        dplyr::filter(any(source == "INPATIENT")) %>% 
        dplyr::filter(!source %in% "INPATIENT") %>%
        dplyr::ungroup() %>% 
        dplyr::select(-dupe_count, -year)

clean_prioritize_hosp # obs to be removed

clean_df_step2 <-
    clean_df_step1 %>% 
      dplyr::setdiff(clean_prioritize_hosp) 

# Prioritize RME over ambulatory
clean_prioritize_rme <-
  clean_df_step2 %>% 
      dplyr::mutate(year = lubridate::year(d_event)) %>% 
        janitor::get_dupes(studyid, year) %>% 
        group_by(studyid, year) %>% 
        dplyr::filter(!any(source == "INPATIENT")) %>% # exclude strata with inpatient
        dplyr::filter(any(source == "RME")) %>%
        dplyr::filter(!source %in% "RME") %>%
        dplyr::ungroup() %>% 
        dplyr::select(-dupe_count, -year)

clean_df_step3 <-
    clean_df_step2 %>% 
      dplyr::setdiff(clean_prioritize_rme) 


# Retain first observation in subjectid-year stratum

drop_repeat_vists <-
  clean_df_step3 %>% 
    dplyr::mutate(year = lubridate::year(d_event)) %>% 
    janitor::get_dupes(studyid, year) %>%
    dplyr::group_by(studyid, year) %>%
    dplyr::arrange(d_event) %>% 
    dplyr::filter(!row_number() == 1) %>% 
    dplyr::ungroup() %>% 
    dplyr::select(-dupe_count, -year)

# Join with `persons` df for bmi
encounters_casedef <-  
  clean_df_step3 %>% 
    dplyr::setdiff(drop_repeat_vists) %>% 
    dplyr::left_join(persons, by = "studyid")

# write_rds(encounters_casedef, "data/encounters_casedef.rds")

# encounters_casedef <-  
#   read_rds("data/encounters_casedef.rds")


# remove interim data cleaning objects
rm(encounters_no_other, clean_df_step1, clean_df_step2, clean_df_step3, drop_repeat_vists, clean_non_heat_stroke, clean_prioritize_hosp, clean_prioritize_rme)
```


## Plot case definition dataset (including "other" HSI)
```{r}
encounters_casedef  %>% 
  mutate(year = lubridate::year(d_event)) %>% 
  group_by(year, source, hsi) %>% 
  summarise(n = dplyr::n()) %>% 
  ggplot(aes(x = year, y = n, color = hsi)) +
    geom_point() +
    geom_line() +
  facet_wrap(~source)


encounters_casedef %>% 
  ggplot(aes(x = hsi)) +
    geom_bar(stat = "count") + 
    stat_count(geom = "text", colour = "white", size = 5,
    aes(label = ..count..),position = position_stack(vjust = 0.5)) +
    coord_flip() +
    theme_bw() +
    theme(axis.text.y = element_text(size = 15)) 


```

```{r}
encounters_casedef <-
  read_rds("data/encounters_casedef.rds")

```

