---
title: "data_import"
author: "SL"
date: "5/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(Hmisc)
library(janitor)
library(skimr)
library(zoo)
library(naniar)

# packrat::snapshot()
```

## Import data files

HSI Data: sas7bdat format
DMIS IS Data: Excel format
```{r}

persons <-
  haven::read_sas("./data/R200131_persons.sas7bdat") %>%
  haven::zap_formats() %>% 
  haven::zap_label() %>%
  dplyr::mutate_at(vars(-BMI), haven::zap_empty) %>%  # convert empty character strings into missing values
  janitor::clean_names()


encounters <-
  haven::read_sas("./data/R200131_encounters.sas7bdat") %>%
  haven::zap_formats() %>% 
  haven::zap_label() %>% # remove SAS labels
  dplyr::mutate_at(vars(-D_EVENT), haven::zap_empty) %>%  # convert empty character strings into missing values
  janitor::clean_names() %>% 
  unique()   # remove duplicate rows 

# inspect missing values
encounters %>% 
  naniar::vis_miss(warn_large_data = FALSE)  
  
dmisid <- readxl::read_excel("./data/DMISID_FY2019.xlsx") %>% 
  janitor::clean_names() %>% 
  dplyr::select(dmis_id, 
                facility_unit_id = unit_id_code,
                facility_type = facility_type_code_6_char_maximum,
                facility_name = dmis_facility_name_30_character_maximum,
                facility_installation = installation_name_35_character_maximum, 
                facility_state = facility_state_code,
                facility_city = facility_city_name_32_character_maximum,
                facility_zipcode = facility_5_digit_zip_code,
                facility_region = health_service_region,
                facility_branch = branch_of_service_authority_code)


```


## Clean Data

## Multiple Encounters

For individuals who meet the case definition:
• The incidence date is considered the date of the first hospitalization, outpatient medical encounter, or reportable medical event that includes a defining diagnosis of heat illness.
• An individual is considered an incident case only once per calendar year.
• For individuals with more than one heat illness diagnosis in a calendar year, heat stroke is prioritized over heat exhaustion.
• Medical encounters for each individual within a calendar year are prioritized: hospitalizations > reportable medical events > ambulatory visits.
```{r}

encounters %>% 
  group_by(studyid) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  summary(n)


encounters %>% 
  group_by(studyid) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  ggplot() +
    geom_histogram(aes(x = n), bins = 75)


# Classify each encounter as heat stroke, heat exhaustion, or other

encounters_diag <-
  encounters %>% 
   dplyr::mutate(hsi = dplyr::case_when(
     str_detect(dx1, "T670XX[A-Z]") | str_detect(dx1, "9920") |
     str_detect(dx2, "T670XX[A-Z]") | str_detect(dx2, "9920")
     ~ "heat_stroke",
     str_detect(dx1, "T67[3459]XX[A-Z]") | str_detect(dx1, "992[345]") |
     str_detect(dx2, "T67[3459]XX[A-Z]") | str_detect(dx2, "992[345]")
     ~ "heat_exhaustion",
        TRUE ~ "other")) 


encounters_diag %>% 
  count(hsi)

encounters_diag %>% 
  dplyr::group_by(source) %>% 
  count(hsi)

# Apply case definition: 
#   considered an incident case only once per calendar year
#   heat stroke is prioritized over heat exhaustion


# Identify observations to remove: 
#   more than 1 observation per studyid-year
#   heat stroke > heat exhaustion
#   hospitalizations > reportable medical events > ambulatory visits


# Remove `other` hsi observations 

encounters_no_other <-
  encounters_diag %>% 
    dplyr::filter(!hsi %in% "other")


# Remove `heat_exhaustion` or `other` if `heat_stroke` in studyid/year stratum

clean_non_heat_stroke <-
  encounters_no_other %>% 
    dplyr::mutate(year = lubridate::year(d_event)) %>% 
    janitor::get_dupes(studyid, year) %>% 
    group_by(studyid, year) %>% 
    dplyr::filter(any(hsi == "heat_stroke")) %>% 
    dplyr::filter(!hsi %in% "heat_stroke") %>%
    dplyr::ungroup() %>% 
    dplyr::select(-dupe_count, -year)


clean_df_step1 <-
    encounters_no_other %>% 
      dplyr::setdiff(clean_non_heat_stroke)  # remove rows that appear in `clean_non_heat_stroke`
  
 # Prioritize Hospitalizations
 
clean_prioritize_hosp <-
  clean_df_step1 %>% 
      dplyr::mutate(year = lubridate::year(d_event)) %>% 
        janitor::get_dupes(studyid, year) %>% 
        group_by(studyid, year) %>% 
        dplyr::filter(any(source == "INPATIENT")) %>% 
        dplyr::filter(!source %in% "INPATIENT") %>%
        dplyr::ungroup() %>% 
        dplyr::select(-dupe_count, -year)

clean_df_step2 <-
    clean_df_step1 %>% 
      dplyr::setdiff(clean_prioritize_hosp) 

# Prioritize RME over ambulatory
clean_prioritize_rme <-
  clean_df_step2 %>% 
      dplyr::mutate(year = lubridate::year(d_event)) %>% 
        janitor::get_dupes(studyid, year) %>% 
        group_by(studyid, year) %>% 
        dplyr::filter(!any(source == "INPATIENT")) %>% # exclude strata with inpatient
        dplyr::filter(any(source == "RME")) %>%
        dplyr::filter(!source %in% "RME") %>%
        dplyr::ungroup() %>% 
        dplyr::select(-dupe_count, -year)

clean_df_step3 <-
    clean_df_step2 %>% 
      dplyr::setdiff(clean_prioritize_rme) 


# Retain first observation in subjectid-year stratum

drop_repeat_vists <-
  clean_df_step3 %>% 
    dplyr::mutate(year = lubridate::year(d_event)) %>% 
    janitor::get_dupes(studyid, year) %>%
    dplyr::group_by(studyid, year) %>%
    dplyr::arrange(d_event) %>% 
    dplyr::filter(!row_number() == 1) %>% 
    dplyr::ungroup() %>% 
    dplyr::select(-dupe_count, -year)

# Join with `persons` df for bmi
encounters_casedef <-  
  clean_df_step3 %>% 
    dplyr::setdiff(drop_repeat_vists) %>% 
    dplyr::left_join(persons, by = "studyid")

# write_rds(encounters_casedef, "data/encounters_casedef.rds")



# remove interim data cleaning objects
rm(encounters_no_other, clean_df_step1, clean_df_step2, clean_df_step3, drop_repeat_vists, clean_non_heat_stroke, clean_prioritize_hosp, clean_prioritize_rme)
```



## Dataset Summaries: General
```{r}

Hmisc::describe(encounters)

Hmisc::describe(persons)

skimr::skim(dmisid)


```



## All encounters by date and type

```{r}

encounters %>%
  group_by(d_event, source) %>% 
  summarise(n = dplyr::n()) %>% 
  ggplot(aes(x = d_event, y = n, color = source)) +
    geom_point() +
    geom_line() 


encounters %>%
  group_by(d_event, source) %>% 
  summarise(n = dplyr::n()) %>% 
  ggplot(aes(x = d_event, y = n)) +
    geom_point() +
    geom_line() +
    facet_wrap(~source)


# By Year-Month
encounters %>% 
  mutate(year_mon = zoo::as.yearmon(d_event)) %>% 
  group_by(year_mon, source) %>% 
  summarise(n = dplyr::n()) %>% 
  ggplot(aes(x = year_mon, y = n, color = source)) +
    geom_point() +
    geom_line() 

# By Year
encounters %>% 
  mutate(year = lubridate::year(d_event)) %>% 
  group_by(year, source) %>% 
  summarise(n = dplyr::n()) %>% 
  ggplot(aes(x = year, y = n, color = source)) +
    geom_point() +
    geom_line()   
```
