---
title: "descriptive"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(survival)
library(splines)
library(broom)
library(dlnm)
library(plotly)
library(lubridate)
library(corrplot)
library(table1)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
library(lwgeom)
library(cowplot)
library(tmap)
library(raster)
library(sf)
library(maps)
library(ggspatial)
library(ggrepel)

```


```{r}

daily_indices <- read_rds(file = "data/daily_indices.rds")


# daily_indices <- read_rds(file = "E:/data/daily_indices.rds") %>% 
#   rename(date = `lubridate::date(local_dttm)`) %>% 
#   mutate(wbgt_f_mean = weathermetrics::celsius.to.fahrenheit(wbgt_u_mean),
#          installation = recode(installation, 
#                 `pensacola_nas` = "pensacola",
#                 `portsmouth_nmc` = "portsmouth"))

# write_rds(daily_indices, file = "data/daily_indices.rds")


cc_exposure_df <-
  read_rds(file = "data/cc_exposure_df.rds")

# cc_exposure_df <-
#   read_rds(file = "E:/data/cc_exposure_df.rds") %>% 
#   mutate(wbgt_f_mean = weathermetrics::celsius.to.fahrenheit(wbgt_u_mean))


cc_exposure_df %>% 
  count(cc_exposure_df) %>% View() #24 installations


cc_exposure_df <-
  cc_exposure_df %>% 
     mutate(installation_name = as_factor(installation_name),
       installation_name = recode(installation_name,
        "mcb_camp_lejeune" = "camp_lejeune",
        "mcb_camp_pendleton" = "camp_pendleton",
        "fort_benning_ga" = "fort_benning",
        "fort_sam_houston" = "jbsa",
        "mcrd_beaufort_parris_island" = "parris_island",
        "mcb_quantico" = "quantico",
        "twentynine_palms_main_base" = "twentynine_palms")) 


# write_rds(cc_exposure_df, file = "data/cc_exposure_df.rds")
# write_rds(daily_indices, file = "data/daily_indices.rds")

```





### Counts by service - installation
```{r}

base_service_counts <-
  cc_exposure_df %>% 
    count(installation_name, service) %>% 
    spread(service, n, fill = 0) 


# rank case occurrence by service for each installation; filter top

base_service_rank <-
  cc_exposure_df %>% 
    count(installation_name, service) %>% 
    group_by(installation_name) %>% 
    mutate(rank = rank(-n)) %>% 
    filter(rank == 1)

base_service_df <-
  base_service_counts %>% 
    right_join(base_service_rank %>% 
                 dplyr::select(installation_name, service), by = "installation_name") 


base_service_df %>% 
  count(service)

```

### Geographic / climate region

https://www.ncdc.noaa.gov/monitoring-references/maps/us-climate-regions.php

Through climate analysis, National Centers for Environmental Information scientists have identified nine climatically consistent regions within the contiguous United States which are useful for putting current climate anomalies into a historical perspective (Karl and Koss, 1984).



```{r}

base_service_df$installation_name

# Assign U.S. Climate regions

## 1st column
installation_name <- base_service_df$installation_name 
## 2nd column
region <- c("Southeast", "Southeast", "Southeast", "Southeast", "Ohio Valley", "South", 
            "Southeast", "West", "South", "West", "Southeast", "South",
            "Southeast", "West", "South", "Ohio Valley", "South", "West",
            "Ohio Valley", "South", "Southeast", "Southeast", "Southeast", "Southeast"
            )

climate_regions <- data.frame(installation_name, region) %>% 
  as_tibble()
  

base_service_df <- 
  base_service_df %>% 
    right_join(climate_regions, by = "installation_name") 


base_service_df <-
  base_service_df %>% 
    mutate(service = recode(service,
          "A" = "Army",
          "C" = "Coast Guard",
          "F" = "Air Force",
          "M" = "Marine Corps",
          "N" = "Navy"))


#write_rds(base_service_df, file = "data/base_service_df.rds")
  


base_service_df %>% 
  ggplot(aes(region)) +
    geom_bar() +
    theme_bw()


base_service_df %>% 
  ggplot(aes(region, fill = service)) +
    geom_bar(position = position_dodge()) +
    theme_bw()


# Cross-tab service and region
base_service_df %>% 
  group_by(service, region) %>% 
  summarise(n = n()) %>% 
  spread(region, n)

base_service_df %>% 
  group_by(service, region) %>% 
  summarise(n = n()) %>% 
  spread(region, n) %>% 
  knitr::kable()
```


## Outcome table
```{r}

to_table1 <-
  cc_exposure_df %>% 
    filter(case == 1) %>% 
    dplyr::select(installation_name, source, age, sex, race_ethnic, service, grade, hsi) %>% 
       mutate(service = recode(service,
            "A" = "Army",
            "C" = "Coast Guard",
            "F" = "Air Force",
            "M" = "Marine Corps",
            "N" = "Navy"),
            source = recode(source,
            "INPATIENT" = "In-Patient",
            "OUTPATIENT" = "Out-Patient",
            "RME" = "Reportable Event"),
            hsi = recode(hsi,
            "heat_exhaustion" = "Heat Exhaustion",
            "heat_stroke" = "Heat Stroke"),
            sex = recode(sex,
            "F" = "Female",
            "M" = "Male",
            "Z" = "Unknown")
            ) %>% 
  left_join(climate_regions, by = "installation_name") %>% 
  mutate_if(is.character, as.factor) %>% 
            mutate(age = fct_relevel(age, ">=40", after = Inf))


label(to_table1$hsi) <- "HSI Diagnosis"
label(to_table1$age) <- "Age Group"
label(to_table1$sex) <- "Sex"
label(to_table1$race_ethnic) <- "Race/Ethnicity"
label(to_table1$grade) <- "Grade Group"
label(to_table1$service) <- "Service Branch"
label(to_table1$region) <- "NOAA NCEI Climate Region"


table1::table1(~ hsi + sex + age + sex + grade + race_ethnic  | source, data = to_table1)
table1::table1(~ hsi + sex + age + sex + grade   | source, data = to_table1)  
table1::table1(~ service + region + race_ethnic | source, data = to_table1)

table1::table1(~ factor(hsi) + factor(age) + factor(sex) + 
               factor(race_ethnic) + factor(grade) | factor(source), data = to_table1)
  

```


## Exposures

```{r}

#Density plot, all case days 1998-2018

to_density_plot <-
  cc_exposure_df %>%
    filter(case == 1) %>% 
    dplyr::select(installation_name, d_event, wbgt_mean, wbgt_max) %>% 
    mutate("Mean WBGT" = weathermetrics::celsius.to.fahrenheit(wbgt_mean),
           "Max WBGT" = weathermetrics::celsius.to.fahrenheit(wbgt_max)) %>% 
    dplyr::select(installation_name, `Mean WBGT`, `Max WBGT`) %>% 
    pivot_longer(-installation_name, names_to = "Index", values_to = "Value")
  
#check for missing values
  to_density_plot[!complete.cases(to_density_plot),] %>% View()
  
  
to_density_plot %>%   
  ggplot(aes(x = Value, fill = Index, colour = Index)) +
      geom_density(alpha = 0.5) +
      geom_rug() +
      theme_bw() +
  labs(title = "Density plot of daily indices on all case days, 1998-2019",
       x = "Daily Index Value (°F)")



## Day of year

cc_exposure_df %>%
  filter(case == 1) %>% 
  dplyr::select(installation_name, date) %>% 
  mutate(`Day of Year` = lubridate::yday(date)) %>% 
  ggplot(aes(x = `Day of Year`)) +
  geom_density(colour = "cadetblue", fill = "cadetblue", alpha = 0.5) +
  theme_bw() +
  labs(title = "Day of year for HSI case days, 1998-2019")
    

cc_exposure_df %>%
  filter(case == 1) %>% 
  dplyr::select(installation_name, date) %>% 
  mutate(`Day of Year` = lubridate::yday(date)) %>% 
  ggplot(aes(x = `Day of Year`)) +
  geom_bar(colour = "cadetblue", fill = "cadetblue", alpha = 0.5) +
  theme_bw() +
  labs(title = "Day of year for HSI case days, 1998-2019")

```





## Map

```{r}

centroid_coords <-
  read_rds("E:/data/centroid_coords.rds")


centroid_coords$site_name 
centroid_coords$geometry 

# convert Installation names from snake-case to "title"
base_service_df <-
  base_service_df %>%
    mutate(installation_name = str_replace_all(installation_name, "_", " "),
      installation_name = str_to_title(installation_name, locale = "en"))

base_service_df$installation_name


# Change `centroid_coords` site names to match

centroid_coords <-
  centroid_coords %>% 
    mutate(site_name = recode(site_name,
                              "Fort Benning GA" = "Fort Benning",
                              "NAS Pensacola" = "Pensacola",
                              "Naval Medical Center Portsmouth" = "Portsmouth",
                              "MCB Quantico" = "Quantico",
                              "MCRD San Diego" = "Mcrd San Diego",
                              "NTC and Fort Irwin" = "Ntc And Fort Irwin",
                              "Twentynine Palms Main Base" = "Twentynine Palms",
                              "MCB Camp Lejeune" = "Camp Lejeune",
                              "Eglin AFB" = "Eglin Afb",
                              "Fort Sam Houston" = "Jbsa",
                              "MCRD Beaufort Parris Island" = "Parris Island",
                              "MCB Camp Pendleton" = "Camp Pendleton"))


mapping_df <-
  base_service_df %>% 
    left_join(centroid_coords, by = c("installation_name" = "site_name"))

#write_rds(mapping_df, file = "data/mapping_df.rds")
                              


mapping_df                              

```


```{r}

point_coords <-
  st_coordinates(mapping_df$centroid) %>% 
    as_tibble() %>% 
    rename("longitude" = "X",
           "latitude" = "Y")


mapping_df <-
  mapping_df %>% bind_cols(
    point_coords)



sites <- data.frame(names = mapping_df$installation_name,
                    longitude = mapping_df$longitude,
                    latitude = mapping_df$latitude,
                    region = mapping_df$region,
                    service = mapping_df$service)


sites <- st_as_sf(sites, coords = c("longitude", "latitude"), remove = FALSE, 
    crs = 4326, agr = "constant")



#world map

world <- ne_countries(scale = "medium", returnclass = "sf")
usa <- ne_countries(country = 'united states of america', scale = "medium", returnclass = "sf")
usa

states <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
states




ggplot(data = usa) +
    geom_sf() +
    geom_sf(data = states, fill = "cornsilk") + 
    geom_point(data = sites, aes(x = longitude, y = latitude, fill = service), size = 4, 
        shape = 23) +
    geom_sf(data = sites) +
    geom_text_repel(data = sites, aes(x = longitude, y = latitude, label = names), fontface = "bold", size = 3, 
        nudge_x = 3, nudge_y = -2) +
    coord_sf(xlim = c(-130, -65), ylim = c(24.5, 50), expand = FALSE) +
    ggtitle("Study Installations", subtitle = "(n=24)") +
    theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "azure2"))

ggsave("output/study_map.png")

```





#####################################################################

## Earlier descriptive review
Read in daily NLDAS

```{r}

daily_nldas <- read_rds(file = "E:/data/daily_nldas.rds")

```


"Table 1"

```{r}


# Outcomes 

cc_exposure_df <-
  read_rds(file = "E:/data/cc_exposure_df.rds")

table1::table1(~ factor(source) + factor(hsi) + factor(service) | case, data = cc_exposure_df)


table1::table1(~ factor(installation_name) | case, data = cc_exposure_df)


# Exposure

nldas_1998 <- daily_nldas %>% 
  filter(lubridate::year(date) %in% 1998:2019)

table1::table1(~ tmp_f_mean + heat_index_mean + Twbg_u_mean | factor(installation), data = nldas_1998)

# Indiv risk factors

table1::table1(~ factor(sex) + factor(age) + factor(grade) + bmi | case, data = cc_exposure_df)


```


Compare WBGT to Temp and Heat Index 
```{r}


daily_nldas %>% 
  drop_na %>% 
  filter(lubridate::year(date) %in% 1998:2019) %>% 
  dplyr::select(tmp_f_mean, heat_index_mean, Twbg_u_mean, Tnwb_u_mean) %>% 
  ggplot(aes(x = tmp_f_mean, y = Twbg_u_mean, color = installation)) +
    geom_point(aes(alpha = 0.2, size = 0.2)) +
    geom_smooth(method = "lm") +
    theme_bw()



daily_nldas %>% 
  ungroup() %>% 
  filter(lubridate::year(date) %in% 1998:2019) %>% 
  dplyr::select(tmp_f_mean, heat_index_mean, Twbg_u_mean, Tnwb_u_mean) %>% 
  cor()


daily_nldas %>% 
  filter(lubridate::year(date) %in% 1998:2019) %>% 
  dplyr::select(installation, tmp_f_mean, heat_index_mean, Twbg_u_mean, Tnwb_u_mean) %>% 
  group_by(installation) %>% 
    summarise(r = cor(tmp_f_mean, Twbg_u_mean)) %>% View()

  



```

