---
title: "dlnm"
author: "SL"
date: "10/19/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(survival)
library(splines)
library(broom)
library(dlnm)
library(plotly)


```


## Load daily NLDAS indices

```{r}

nldas_daily <- read_rds("C:/Users/slewa/Projects/heat_stress/data/nldas_daily.rds")

nldas_daily 

nldas_daily %>% count(installation) %>% View()


```

## Load case-control strata

```{r}

case_control_df <-
  read_rds("data/case_control_df.rds")

case_control_df %>% count(installation_name) %>% View()

case_control_df <-
  case_control_df %>% 
    mutate(installation_name = 
     recode(installation_name,
      "CAMP LEJEUNE" = "mcb_camp_lejeune",
      "CAMP PENDLETON" = "mcb_camp_pendleton",
      "EGLIN AFB" = "eglin_afb",
      "FT BENNING" = "fort_benning_ga",
      "FT BLISS" = "fort_bliss",
      "FT BRAGG" = "fort_bragg",
      "FT CAMPBELL" = "fort_campbell",
      "FT GORDON" = "fort_gordon",
      "FT HOOD" = "fort_hood",
      "FT IRWIN" = "ntc_and_fort_irwin",
      "FT JACKSON" = "fort_jackson",
      "FT KNOX" = "fort_knox",
      "FT LEONARD WOOD" = "fort_leonard_wood",
      "FT POLK" = "fort_polk",
      "FT RILEY" = "fort_riley",
      "FT SILL" = "fort_sill",
      "FT STEWART" = "fort_stewart",
      "JBSA" = "fort_sam_houston",
      "PARRIS ISLAND" = "mcrd_beaufort_parris_island",
      "PENSACOLA" = "pensacola",
      "PORTSMOUTH" = "portsmouth",
      "QUANTICO" = "mcb_quantico",
      "SAN DIEGO" = "mcrd_san_diego",
      "TWENTYNINE PALMS" = "twentynine_palms_main_base"
    ))
```


## Join case-crossover and daily exposures

```{r}

cc_exposure_df <-
  case_control_df %>% 
    left_join(nldas_daily,  by = c("installation_name" = "installation", "d_event" = "date")) %>% 
    filter(year %in% 1998:2019)

```

## Conditional Logistic Model (no lag)

Inspect data, compare case days and control days
```{r}

cc_exposure_df %>% 
  count(case)
108248/31647 #3.42 cases per control




# Mean_WBGT

cc_exposure_df %>%
  group_by(installation_name, case) %>% 
  summarise(mean_wbgt = mean(wbgt_f_mean))

cc_exposure_df %>%
  group_by(installation_name, case) %>% 
  summarise(mean_wbgt = mean(wbgt_f_mean)) %>%
  filter(case == 1) %>% 
  drop_na() %>%
  ungroup() %>% 
  mutate(installation_name = fct_reorder(installation_name, desc(mean_wbgt))) %>%   ggplot(aes(x = installation_name, y = mean_wbgt)) +
    geom_col() +
    theme_bw() +
      theme(axis.text.x = element_text(angle = 90))



# boxplots
cc_exposure_df %>%
  group_by(installation_name) %>% 
  filter(case == 1,
         installation_name %in% c(
           "fort_benning_ga",
           "fort_bragg",
           "mcb_camp_lejeune",
           "mcrd_beaufort_parris_island",
           "fort_campbell"
                    )) %>%
  mutate(installation_name = recode(installation_name,
                                    "fort_benning_ga" = "FT BENNING",
                                    "fort_bragg" = "FT BRAGG",
                                    "mcb_camp_lejeune" = "CP LEJEUNE",
                                    "mcrd_beaufort_parris_island" = "PARRIS ISLAND",
                                    "fort_campbell" = "FT CAMPBELL")) %>% 
  ggplot(aes(x = installation_name, y = wbgt_f_mean)) +
    geom_boxplot() +
    theme_bw() +
      #theme(axis.text.x = element_text(angle = 90)) +
      labs(y = "Mean WBGT (°F)",
           x = "Installation",
           title = "Mean WBGT on day of HSI cases",
            subtitle = "1998 - 2019")
  


# Max WBGT
#
cc_exposure_df %>%
  group_by(installation_name) %>% 
  filter(case == 1,
         installation_name %in% c(
           "fort_benning_ga",
           "fort_bragg",
           "mcb_camp_lejeune",
           "mcrd_beaufort_parris_island",
           "fort_campbell"
                    )) %>%
  mutate(installation_name = recode(installation_name,
                                    "fort_benning_ga" = "FT BENNING",
                                    "fort_bragg" = "FT BRAGG",
                                    "mcb_camp_lejeune" = "CP LEJEUNE",
                                    "mcrd_beaufort_parris_island" = "PARRIS ISLAND",
                                    "fort_campbell" = "FT CAMPBELL")) %>% 
  ggplot(aes(x = installation_name, y = wbgt_f_max)) +
    geom_boxplot() +
    theme_bw() +
      #theme(axis.text.x = element_text(angle = 90)) +
      labs(y = "Max WBGT (°F)",
           x = "Installation",
           title = "Maximum WBGT on day of HSI cases",
            subtitle = "1998 - 2019")



```



# CLM

- CLM all data
- CLM restrict winter months (DEC, JAN, FEB)
- CLM mean WBGT > 50
```{r}


clm_basic <- 
   survival::clogit(case ~ ns(wbgt_f_mean, df = 2) +  
                   strata(date), 
                   method = "efron", 
                   cc_exposure_df) 

# summary(clm_basic)


# broom::tidy(clm_basic)
# broom::glance(clm_basic)

clm_augment <-
  broom::augment(clm_basic, cc_exposure_df)



clm_augment %>% 
  ggplot(aes(x = wbgt_f_mean, y = .fitted)) + 
  geom_smooth(size = 1.5) + # method = 'gam' and formula 'y ~ s(x, bs = "cs")'
  geom_point(alpha = 0.05, size = 0.5) +
  theme_bw() +
    ylab("Odds of HSI")
  


###############################################################################################

# Remove winter months (Dec, Jan, Feb)

cc_exposure_mar_nov <-
  cc_exposure_df %>% 
    filter(!lubridate::month(d_event) %in% c(12, 01, 02))



clm_basic_mar_nov <- 
   survival::clogit(case ~ ns(wbgt_f_mean, df = 2) +  
                   strata(date), 
                   method = "efron", 
                   cc_exposure_mar_nov) 



clm_augment_mar_nov <-
  broom::augment(clm_basic_mar_nov, cc_exposure_mar_nov)



clm_augment_mar_nov %>% 
  ggplot(aes(x = wbgt_f_mean, y = .fitted)) + 
  geom_smooth(size = 1.5) + # method = 'gam' and formula 'y ~ s(x, bs = "cs")'
  geom_point(alpha = 0.05, size = 0.5) +
  theme_bw() +
    ylab("Odds of HSI") +
    ggtitle("CLM, ns 2df, MAR - NOV")
  

#########################################

# Filter WBGT mean less than 50 deg F


cc_exposure_gt50 <-
  cc_exposure_df %>% 
     group_by(studyid, d_event, installation_name) %>%  
        filter(any(wbgt_f_mean > 50)) %>% 
        ungroup()



clm_basic_gt50 <- 
   survival::clogit(case ~ ns(wbgt_f_mean, df = 2) +  
                   strata(date), 
                   method = "efron", 
                   cc_exposure_gt50) 



clm_basic_augment_gt50 <-
  broom::augment(clm_basic_gt50, cc_exposure_gt50)



clm_basic_augment_gt50 %>% 
  ggplot(aes(x = wbgt_f_mean, y = .fitted)) + 
  geom_smooth(size = 1.5) + # method = 'gam' and formula 'y ~ s(x, bs = "cs")'
  geom_point(alpha = 0.05, size = 0.5) +
  theme_bw() +
    ylab("Odds of HSI") +
    ggtitle("CLM, ns 2df, WBGT mean > 50")

```


# Examine linear fit

- mean WBGT gt 50 deg F
```{r}


cc_exposure_gt50 



clm_basic_gt50_lin <- 
   survival::clogit(case ~ wbgt_f_mean +  
                   strata(date), 
                   method = "efron", 
                   cc_exposure_gt50) 



clm_basic_augment_gt50_lin <-
  broom::augment(clm_basic_gt50_lin, cc_exposure_gt50)



clm_basic_augment_gt50_lin %>% 
  ggplot(aes(x = wbgt_f_mean, y = .fitted)) + 
  geom_smooth(method = "lm", size = 1.5) +
  geom_point(alpha = 0.05, size = 0.5) +
  theme_bw() +
    ylab("Odds of HSI") +
    ggtitle("CLM, linear, WBGT mean > 50")

```


# DLNM

## Lags function



```{r}

lags <- seq(7) # Number of lags

lag_names <- paste("lag", formatC(lags, width = nchar(max(lags)), flag = "0"), 
  sep = "_")

lag_fun <- setNames(paste("dplyr::lag(., ", lags, ")"), lag_names)

#  d %>% mutate_at(vars(x), funs_(lag_fun))

```


```{r}


# for nested df by installation, with date in 1st column and index in 2nd 

create_lags_fun = function(df) {
  
  df %>% 
    mutate(lag_1 = dplyr::lag(dplyr::select(2), n = 1),
           lag_2 = dplyr::lag(dplyr::select(2), n = 2),
           lag_3 = dplyr::lag(dplyr::select(2), n = 3),
           lag_4 = dplyr::lag(dplyr::select(2), n = 4),
           lag_5 = dplyr::lag(dplyr::select(2), n = 5),
           lag_6 = dplyr::lag(dplyr::select(2), n = 6),
           lag_7 = dplyr::lag(dplyr::select(2), n = 7))
  
}

```

## Cross-basis


```{r}

selected_index <- "wbgt_f_mean"


# create lag matrix

lag_matrix_all <-
   nldas_daily %>% 
    filter(date %in% as.Date("1997-12-15"):as.Date("2019-12-31")) %>% 
      dplyr::select(installation, date, selected_index) %>% 
   group_by(installation) %>% 
   mutate_at(vars(selected_index), funs_(lag_fun)
  )





# join lag matrix to case-crossover dataframe

cc_lag_matrix <-
  cc_exposure_df %>% 
    filter(year %in% 1998:2019) %>% 
    dplyr::select(!selected_index) %>%    # remove to avoid double listeing after join
    left_join(lag_matrix_all,  by = c("installation_name" = "installation", "date" = "date")) 


cc_lag_only <- 
  cc_lag_matrix %>% 
  dplyr::select(selected_index, lag_1:lag_7)



# create dlnm cross-basis

wbgt_mean_cb <-
    crossbasis(
      cc_lag_only,    
      lag = 7,    # of lags
      argvar = list(fun = "ns", df = 3),    #  functional form of the dose-response curve
      arglag = list(fun = "ns", df = 3))    #  functional form of the lags

summary(wbgt_mean_cb)



```

```{r}
# run model and get prediction for wbgt_mean


cc_exposure_df <-   cc_exposure_df %>% 
  mutate(stratum = paste(studyid, d_event, sep = " "))


wbgt_mean_dlnm <- survival::clogit(case ~ 
                  wbgt_mean_cb +  # lagged, nonlinear term for exposure
                  strata(stratum), 
                  method = "efron", 
                  data =  cc_exposure_df) 


pred_wbgt_mean <- crosspred(wbgt_mean_cb, wbgt_mean_dlnm, cumul = TRUE)



```

Plot cross-predictions
```{r}

# 3d Plot 

plot(pred_wbgt_mean, 
     xlab = "\nmean WBGT", zlab = "\nRR", ylab = "\nLag", 
     theta = 40, phi = 30, lphi = 30,
     main = "Mean daily WBGT \n1998-2019")

crosspred_plot <-  
  plot(pred_wbgt_mean, 
       xlab = "\nmean WBGT", zlab = "\nRR", ylab = "\nLag", 
       theta = 40, phi = 30, lphi = 30,
       main = "Mean daily WBGT \n1998-2019")



# Slice Plot
# visualize association at specific lags 


# Plot dose-response curve at Lag 0

par(mar = c(5.1, 4.1, 4.1, 2.1))


```


```{r}

plot(pred_wbgt_mean, "slices",
     lag = 0,
     ylim = c(0.95, 1.6),
     lwd = 4,
     col = "darkred",
     main = "Exposure-Response at Lag 0 \n  1998-2019", 
     xlab = "Mean WBGT", 
     ylab = "HSI Rate Ratio")


plot(pred_wbgt_mean, "slices",
     lag = 1,
     ylim = c(0.95, 1.6),
     lwd = 4,
     col = "darkred",
     main = "Exposure-Response at Lag 1 \n  1998-2019", 
     xlab = "Mean WBGT", 
     ylab = "HSI Rate Ratio")

plot(pred_wbgt_mean, "slices",
     lag = 2,
     ylim = c(0.95, 1.6),
     lwd = 4,
     col = "darkred",
     main = "Exposure-Response at Lag 2 \n  1998-2019", 
     xlab = "Mean WBGT", 
     ylab = "HSI Rate Ratio")

plot(pred_wbgt_mean, "slices",
     lag = 3,
     ci = "n", 
     ylim = c(0.95, 1.6),
     lwd = 2,
     main = "Exposure-Response at Lag 3 \n  1998-2019", 
     xlab = "Mean WBGT", 
     ylab = "HSI Rate Ratio")
```

```{r}
plot(pred_wbgt_mean, "slices",
     var = 60,
     ylim = c(0.95, 1.4),
     lwd = 4,
     col = "darkred",
     main = "Lag-Response at 60°F mean WBGT \n  1998-2019", 
     xlab = "Days Lag", 
     ylab = "HSI Rate Ratio")



```








# join lag matrix to case-crossover dataframe


cc_selected_index <-
  case_control_df %>% 
      filter(year %in% 1998:2019) %>% 
      mutate(installation_name = 
         recode(installation_name,
          "CAMP LEJEUNE" = "mcb_camp_lejeune",
          "CAMP PENDLETON" = "mcb_camp_pendleton",
          "EGLIN AFB" = "eglin_afb",
          "FT BENNING" = "fort_benning_ga",
          "FT BLISS" = "fort_bliss",
          "FT BRAGG" = "fort_bragg",
          "FT CAMPBELL" = "fort_campbell",
          "FT GORDON" = "fort_gordon",
          "FT HOOD" = "fort_hood",
          "FT IRWIN" = "ntc_and_fort_irwin",
          "FT JACKSON" = "fort_jackson",
          "FT KNOX" = "fort_knox",
          "FT LEONARD WOOD" = "fort_leonard_wood",
          "FT POLK" = "fort_polk",
          "FT RILEY" = "fort_riley",
          "FT SILL" = "fort_sill",
          "FT STEWART" = "fort_stewart",
          "JBSA" = "fort_sam_houston",
          "PARRIS ISLAND" = "mcrd_beaufort_parris_island",
          "PENSACOLA" = "pensacola",
          "PORTSMOUTH" = "portsmouth",
          "QUANTICO" = "mcb_quantico",
          "SAN DIEGO" = "mcrd_san_diego",
          "TWENTYNINE PALMS" = "twentynine_palms_main_base"
        )) %>% 
      left_join(lag_matrix, by = c("installation_name" = "installation", "d_event" = "date")) 


