---
title: "dmisid"
author: "SL"
date: "6/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(naniar)
library(purrr)
library(janitor)
library(Hmisc)


```


Download DMIS Year End 1989 - 2019 files from:
https://www.health.mil/Military-Health-Topics/Technology/Support-Areas/Geographic-Reference-Information/DMIS-ID-Tables


```{r}

# List all DMISIS file paths (FY1989 - 2019)
dmisid_file_list <- list.files("data/dmisid/", pattern = '*.xls',   full.names = TRUE)

dmisid_file_list <- setNames(dmisid_file_list, dmisid_file_list) 
  
# Read-in all Excel files
dmisid_df <- map_df(dmisid_file_list, readxl::read_excel, .id = "id")

dmisid_df %>% 
      filter(is.na(`Installation Name`) & is.na(`Installation Name (35-character maximum)`))

dmisid <-
  dmisid_df %>% 
    janitor::clean_names() %>%
    dplyr::select(id, dmis_id, facility_name, dmis_facility_name_30_character_maximum, facility_zip_code, installation_name, installation_name_35_character_maximum, facility_5_digit_zip_code) %>% 
  tidyr::unite(facility_name, facility_name, dmis_facility_name_30_character_maximum, sep = "", na.rm = TRUE) %>% 
  tidyr::unite(installation_name, installation_name, installation_name_35_character_maximum, sep = "", na.rm = TRUE) %>% 
  tidyr::unite(facility_zipcode, facility_zip_code, facility_5_digit_zip_code, sep = "", na.rm = TRUE) %>% 
  dplyr::mutate(dmis_fy = 
                  id %>% stringr::str_match_all("[0-9]+") %>%
                  unlist() %>% as.numeric()) %>% 
  dplyr::select(-id) %>% 
  dplyr::mutate_all(list(~na_if(.,""))) # convert blank values to `NA`

# Inspect missing values

# dmisid %>% 
#     filter(is.na(installation_name))
# 
# dmisid %>% 
#     filter(is.na(facility_zipcode))

# dmisid %>% 
#     filter(is.na(installation_name) & is.na(facility_zipcode))


#dmisid %>% 
#  naniar::vis_miss()  

dmisid %>% 
  group_by(dmis_id) %>% 
  count()

# Keep only one observation for each dmis_id

dmisid_distinct <-
  dmisid %>%
    arrange(desc(dmis_fy)) %>% 
    distinct(dmis_id, .keep_all = TRUE) 
  
# dmisid_distinct %>%   
#   count(dmis_fy)
```

## Link to encounters

```{r}
# Read-in `encounters_casedef`


encounters_casedef <-
  read_rds("data/encounters_casedef.rds") 
    

# # Identify and remove observations with no dmisid
# 
# no_dmisid_casedef <-
#   encounters_casedef %>% 
#   filter(is.na(dmisid))
# 
# # Missing dmisid (location) summary
# Hmisc::describe(no_dmisid_casedef)


# Filter out obs missing `dmidid`, convert N prefixes in `dmisid` to "0" 

encounters_casedef <-
 encounters_casedef %>% 
    filter(!is.na(dmisid)) %>% # filter out observations with no dmisid
    dplyr::mutate(dmisid = stringr::str_replace_all(string = dmisid, pattern = "N", replacement = "0")) %>% 
    dplyr::mutate(year = lubridate::year(d_event))



# Join encounters with DMISID based on table key for each FY

# encounters_casedef <-
#   list(encounters_casedef, dmisid) %>% reduce(left_join, by = c("dmisid" = "dmis_id"))

encounters_casedef_inst <-
  encounters_casedef %>% 
    left_join(dmisid_distinct, by = c("dmisid" = "dmis_id")) 

encounters_casedef_inst


# Inspect missing values
#encounters_casedef %>%
#  dplyr::select(dmisid, facility_name:installation_name) %>% 
#  naniar::vis_miss(warn_large_data = FALSE) 


no_dmisid_match <-
  encounters_casedef_inst %>% 
  filter(is.na(installation_name))

no_dmisid_match %>% 
  group_by(dmisid) %>% 
  count() %>% 
  arrange(desc(n))

# Inspect facility names of DMISIDs missing installation names
no_dmisid_match %>% 
  group_by(facility_name) %>% 
  count() %>% 
  arrange(desc(n))

# DMISID 6133 not in DMIS reference tables, 244 case def observations (Marines)
encounters_casedef_inst %>% 
  filter(dmisid %in% "6133") %>% Hmisc::describe()

encounters_casedef_inst %>% 
  group_by(installation_name) %>% 
  count() %>% 
  arrange(desc(n))

encounters_casedef_inst %>% 
  dplyr::filter(is.na(installation_name)) #965 missing

encounters_casedef_inst %>% 
  dplyr::filter(is.na(facility_zipcode)) #3,850 missing

```


## Clean data - installation names

```{r}
# 485 distinct installation names


# remove `.`, eg `FT.`; 461 distinct,
# change `FORT` to `FT`, 455 distinct

encounters_casedef_inst <-
  encounters_casedef_inst %>% 
    mutate(installation_name = stringr::str_remove(installation_name, "\\."),
           installation_name = stringr::str_replace(installation_name, "FORT", "FT"),# also changes "BEAUFORT"
           installation_name = stringr::str_replace(installation_name, "BEAUFT", "BEAUFORT"))

  
# Join installation names
  
# combine `CAMP LEJUNE` & `CHERRY POINT`
# combine `PARRIS ISLAND` & `BEAUFORT`
# combine `LACKLAND AFB`, `JOINT (AF) SAN ANTONIO LAF-RAF-FSH`, `	FT SAM HOUSTON`, `LACKLAND JBSA`, `LACKLAND JB`, `RANDOLPH AFB`
# 
# FT BRAGG- NC  
# NH TWENTY-NINE PALMS
# SAN DIEGO NH

encounters_casedef_inst <-
  encounters_casedef_inst %>% 
    dplyr::mutate(installation_name =
              dplyr::recode(installation_name, 
                  `CHERRY POINT` = "CAMP LEJEUNE",
                  `BEAUFORT` = "PARRIS ISLAND",
                  `LACKLAND AFB` = "JBSA",
                  `JOINT (AF) SAN ANTONIO LAF-RAF-FSH` = "JBSA",
                  `FT SAM HOUSTON` = "JBSA",
                  `LACKLAND JBSA` = "JBSA",
                  `LACKLAND JB` = "JBSA",
                  `RANDOLPH AFB` = "JBSA",
                  `FT BRAGG- NC` = "FT BRAGG",
                  `NH TWENTY-NINE PALMS` = "TWENTYNINE PALMS",
                  `SAN DIEGO NH` = "SAN DIEGO")  
                  ) 
  


```


## Summarize counts by installation

```{r}
encounters_casedef_inst %>% 
    group_by(installation_name) %>% 
    count() %>% 
    arrange(desc(n)) 


# Top 100 installations
encounters_casedef_inst %>% 
    group_by(installation_name) %>% 
    count() %>% 
    arrange(desc(n)) %>% 
    ungroup() %>% 
    dplyr::slice_head(n = 100) %>% 
  ggplot(aes(x = reorder(installation_name, -n), y = n)) +
    geom_bar(stat = "identity")


# Cumulative percentages


encounters_casedef_inst %>% 
    group_by(installation_name) %>% 
    count() %>% 
    arrange(desc(n)) %>% 
    ungroup() %>% 
    mutate(cum_pct = cumsum(n) / sum(n),
           change_cum_pct = cum_pct - lag(cum_pct)) %>% 
    dplyr::slice_head(n = 50) 


```


# Nest data by installation

Select from Top 27 (cutoff- include Eglin AFB/ next: Schofield, "Eastern Texas", Ft Belvoir); non-included CONUS sites contribute less than 0.7% each to cummulative percentage.
Remove OCONUS locations (Okinawa, Fort Shafter)
```{r}
# Nest by installation

encounters_nest <-
  encounters_casedef_inst %>%
    dplyr::group_by(installation_name) %>% 
    dplyr::group_nest() %>% 
    dplyr::mutate(n = map(data, nrow) %>% unlist()) %>% 
    dplyr::arrange(desc(n)) %>% 
    dplyr::slice_head(n = 27) %>% 
    dplyr::filter(!installation_name %in% c("OKINAWA", "FT SHAFTER")) %>% 
    dplyr::filter(!is.na(installation_name))



# write_rds(encounters_nest, "data/encounters_nest.rds")

```


# Exploratory visualization of cases


## Plots for all case definitions (all locations)

```{r}

# All casedef data, daily TS

encounters_casedef_inst %>%
  dplyr::filter(!hsi %in% "other") %>% 
  dplyr::group_by(d_event) %>% 
  dplyr::summarise(n = n()) %>% 
  ggplot(aes(x = d_event, y = n)) +
    geom_line()  

# All case def data, by year
encounters_casedef_inst %>%
  dplyr::filter(!hsi %in% "other") %>% 
  dplyr::group_by(year) %>%
  filter(!year %in% "2020") %>% 
  dplyr::summarise(n = n()) %>% 
  ggplot(aes(x = year, y = n)) +
    geom_line()  

# All case def data, by year, source

encounters_casedef_inst %>%
  dplyr::filter(!hsi %in% "other") %>% 
  dplyr::group_by(year, source, hsi) %>% 
  dplyr::summarise(n = n()) %>% 
  ggplot(aes(x = year, y = n, color = hsi)) +
    geom_line() +
    facet_wrap(~source, ncol = 1)

```

## Plots for selected CONUS installations (Top 24) 

```{r}

# Selected CONUS installations, cases by year

encounters_nest %>% 
  unnest(data) %>%
  dplyr::filter(!hsi %in% "other") %>% 
  dplyr::group_by(installation_name, year) %>% 
  dplyr::summarise(n = n()) %>% 
  ggplot(aes(x = year, y = n, color = installation_name)) +
    geom_point() +
    geom_smooth(method = lm, alpha = 0.2)


# # Selected, daily TS, by installation
# 
# encounters_nest %>%
#   unnest(data) %>%  
#   dplyr::filter(!hsi %in% "other") %>%
#   dplyr::group_by(d_event, installation_name) %>% 
#   dplyr::summarise(n = n()) %>% 
#   ggplot(aes(x = d_event, y = n, color = installation_name)) +
#     geom_line()  



# # Selected, daily TS
# 
# encounters_nest %>% 
#   unnest(data) %>%  
#   dplyr::filter(!hsi %in% "other") %>%
#   dplyr::group_by(d_event) %>% 
#   dplyr::summarise(n = n()) %>% 
#   ggplot(aes(x = d_event, y = n)) +
#     geom_line()  


# # Selected, by year-mon
# 
# encounters_nest %>% 
#   unnest(data) %>%
#   dplyr::filter(!hsi %in% "other") %>%
#   dplyr::mutate(yearmon = zoo::as.yearmon(d_event)) %>% 
#   dplyr::group_by(yearmon) %>% 
#   dplyr::summarise(n = n()) %>% 
#   ggplot(aes(x = yearmon, y = n)) +
#     geom_line()


# Selected, by outcome source, year-month 

encounters_nest %>% 
  unnest(data) %>%
  dplyr::filter(!hsi %in% "other") %>%
  dplyr::mutate(yearmon = zoo::as.yearmon(d_event)) %>% 
  dplyr::group_by(yearmon, source) %>% 
  dplyr::summarise(n = n()) %>% 
  ggplot(aes(x = yearmon, y = n)) +
    geom_line() +
    facet_wrap(~source, ncol = 1)

# # Selected, by outcome source, year
# 
# encounters_nest %>% 
#   unnest(data) %>%
#   dplyr::filter(!hsi %in% "other") %>%
#   dplyr::group_by(year, source) %>% 
#   dplyr::summarise(n = n()) %>% 
#   ggplot(aes(x = year, y = n)) +
#     geom_line() +
#     facet_wrap(~source, ncol = 1)


```


