---
title: "hourly_indices"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lutz)
library(weathermetrics)
library(devtools)
library(wbgt) #devtools::install_github("mdljts/wbgt")
library(sf) 
library(lubridate)

```


Read-in from external drive
```{r}

nldas_hourly_df <-
  read_rds(file = "D:/data/nldas_hourly_df.rds")

centroid_coords <-
  read_rds(file = "D:/data/centroid_coords.rds")

centroid_coords <-
  read_rds(file = "C:/Users/slewa/OneDrive - cumc.columbia.edu/PhD Files/data/centroid_coords.rds")

#  write_rds(centroid_coords, file = "C:/Users/slewa/OneDrive - cumc.columbia.edu/PhD Files/data/centroid_coords.rds")

nldas_hourly_df %>% 
  count(installation) %>% View()


centroid_coords %>% 
  count(site_name) %>%  View()
```



Identify timezones for local time conversion
```{r}


time_zones <-
  centroid_coords %>% 
  dplyr::select(site_name, centroid) %>% 
  mutate(time_zone = lutz::tz_lookup(centroid, crs = 4326, method = "accurate")) %>% 
  as_tibble() %>% 
  dplyr::select(site_name, time_zone) %>% 
  mutate(site_name = stringr::str_replace_all(site_name, " ", "_"),
         site_name =  stringr::str_to_lower(site_name),
         site_name = recode(site_name, 
                            naval_medical_center_portsmouth = "portsmouth_nmc",
                            nas_pensacola = "pensacola_nas"))
                            
                            
                            

hourly_tz <-
  nldas_hourly_df %>% 
      mutate(utc_dttm = lubridate::ymd_hm(date_time)) %>% 
      dplyr::select(utc_dttm, installation, everything(), -date_time) %>% 
      left_join(time_zones, by = c("installation" = "site_name")) %>%  
      dplyr::mutate(local_dttm = dplyr::case_when(
        .$time_zone == "America/New_York" ~ as.character(with_tz(.$utc_dttm, tz = "America/New_York")),
        .$time_zone == "America/Chicago" ~ as.character(with_tz(.$utc_dttm, tz = "America/Chicago")), 
        .$time_zone == "America/Denver" ~ as.character(with_tz(.$utc_dttm, tz = "America/Denver")),
        .$time_zone == "America/Phoenix" ~ as.character(with_tz(.$utc_dttm, tz = "America/Phoenix")),
        .$time_zone == "America/Los_Angeles" ~ as.character(with_tz(.$utc_dttm, tz = "America/Los_Angeles"))),
        local_dttm = lubridate::ymd_hms(local_dttm)) %>% 
    dplyr::select(utc_dttm, local_dttm, everything(), -time_zone)


hourly_tz[!complete.cases(hourly_tz),]
```


Meteorology conversions and heat index
From original NLDAS variables, add windspeed, temp in F and C, relative humidity, dew point (C), heat index (F)

Restrict RH to 100%

```{r}

hourly_indices <-
  hourly_tz %>% 
    mutate(windspeed = sqrt(UGRD^2 + VGRD^2),
           tmp_f = weathermetrics::convert_temperature(TMP, old_metric = "kelvin", new_metric = "fahrenheit"),
           tmp_c = weathermetrics::convert_temperature(TMP, old_metric = "kelvin", new_metric = "celsius"),
           rh = humidity::SH2RH(SPFH, TMP, p = PRES, isK = TRUE),
           rh = case_when(
             rh > 100 ~ 100,
             rh <= 100 ~ rh
           ),
           dp_c = humidity.to.dewpoint(rh = rh, t = tmp_c, temperature.metric = "celsius"),
           heat_index = weathermetrics::heat.index(t = tmp_f,
                           rh = rh,
                           temperature.metric = "fahrenheit",
                           output.metric = "fahrenheit",
                           round = 2))  




```


Wet Bulb Globe Temperature (WBGT) Estimate


```{r}

lat_lon <-
  centroid_coords %>% 
     mutate(site_name = stringr::str_replace_all(site_name, " ", "_"),
           site_name =  stringr::str_to_lower(site_name),
           site_name = recode(site_name, 
                              naval_medical_center_portsmouth = "portsmouth_nmc",
                              nas_pensacola = "pensacola_nas")) %>% 
    as_tibble() %>% 
    dplyr::select(site_name, centroid) %>%  
    mutate(longitude = unlist(map(centroid,1)),
           latitude = unlist(map(centroid,2))
  ) %>% 
    dplyr::select(-centroid)

write_rds(lat_lon, file = "D:/data/lat_lon.rds")

lat_lon <- read_rds(file = "D:/data/lat_lon.rds")

lat_lon %>% View()
```

WBGT with mdljts wrapper. Create a dataframe with the required columns for the wbgt_df function.


```{r}

hourly_indices <-
  read_rds(file = "D:/data/hourly_indices.rds")

# Create dataframe with columns needed for wbgt::wbgt_df (mdljts wrapper)

                     
# Join lat and lon
hourly_indices <-
  hourly_indices %>% 
  left_join(lat_lon, by = c("installation" = "site_name")) %>% 
  dplyr::select(utc_dttm, local_dttm, installation, longitude, latitude, everything())

hourly_indices 

# write_rds(hourly_indices, file = "D:/data/hourly_indices.rds")

# write_rds(hourly_indices, file = "C:/Users/slewa/OneDrive - cumc.columbia.edu/PhD Files/data/hourly_indices.rds")

# Create dataframe for `wbgt_df` function

wbgt_mdljts_df <-
  hourly_indices %>%
    drop_na %>%  #complete cases (missing a few data points from one hour ~1994)
    mutate(
      year = lubridate::year(local_dttm), 
      month = lubridate::month(local_dttm), 
      day = lubridate::day(local_dttm), 
      hour = lubridate::hour(local_dttm), 
      minute = lubridate::minute(local_dttm), 
      gmt = lubridate::hour(utc_dttm), 
      avg = 60, 
      lat = latitude, 
      lon = longitude, 
      solar = DSWRF, 
      pres = PRES / 100, 
      Tair = tmp_c, 
      relhum = rh, 
      speed = windspeed, 
      zspeed = 10, 
      dT = 0, 
      urban = 0) %>% 
  dplyr::select(year:urban)

wbgt_mdljts_df

write_rds(wbgt_mdljts_df, file = "D:/data/wbgt_mdljts_df.rds")

wbgt_mdljts_df <-
  read_rds(file = "D:/data/wbgt_mdljts_df.rds")


# Execute WBGT wrapper on entire dataframe 

# By dataframe - only returns WBGT, not components (wet bulb)
wbgt_mdljts <-     
 wbgt::wbgt_df(wbgt_mdljts_df) 

write_rds(wbgt_mdljts, file = "D:/data/wbgt_mdljts.rds")


wbgt_mdljts <-
  read_rds("D:/data/wbgt_mdljts.rds")




# Use Urban exponents

wbgt_mdljts_u_df <-
  hourly_indices %>%
    drop_na %>%  #complete cases (missing a few data points from one hour ~1994)
    mutate(
      year = lubridate::year(local_dttm), 
      month = lubridate::month(local_dttm), 
      day = lubridate::day(local_dttm), 
      hour = lubridate::hour(local_dttm), 
      minute = lubridate::minute(local_dttm), 
      gmt = lubridate::hour(utc_dttm), 
      avg = 60, 
      lat = latitude, 
      lon = longitude, 
      solar = DSWRF, 
      pres = PRES / 100, 
      Tair = tmp_c, 
      relhum = rh, 
      speed = windspeed, 
      zspeed = 10, 
      dT = 0, 
      urban = 1) %>% 
  dplyr::select(year:urban)




wbgt_mdljts_u <-     
 wbgt::wbgt_df(wbgt_mdljts_u_df) %>% 
  rename(wbgt_u = wbgt)


write_rds(wbgt_mdljts_u, file = "D:/data/wbgt_mdljts_u.rds")



hourly_nldas <-
  hourly_indices %>%
    drop_na %>% 
    bind_cols(wbgt_mdljts$wbgt) %>% 
    bind_cols(wbgt_mdljts_u$wbgt_u) %>% 
  rename(wbgt = "...18",
         wbgt_u = "...19")

write_rds(hourly_nldas, file = "D:/data/hourly_nldas.rds")

```



Check correlations with temperature
```{r}

hourly_nldas  %>% 
  filter(lubridate::year(local_dttm) %in% 1998:2019) %>% 
  dplyr::select(tmp_f, heat_index, wbgt, wbgt_u) %>% 
  cor()


hourly_nldas  %>% 
  filter(lubridate::year(local_dttm) %in% 1998:2019) %>% 
  dplyr::select(installation, tmp_f, heat_index, wbgt, wbgt_u) %>% 
  group_by(installation) %>% 
    summarise(r = cor(tmp_f, wbgt)) %>% View()

```

