---
title: "knox_extract"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf) 
library(tidyverse)
library(viridis)
library(rvest)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
library(lwgeom)
library(cowplot)
library(purrr)
library(purrrlyr)
library(tmap)
library(raster)
library(ncdf4)
library(ncdump)
library(lubridate)
library(flipTime)
library(fuzzyjoin)
library(RNetCDF)
library(tidync)
library(furrr)
library(humidity)
library(HeatStress) #devtools::install_github("anacv/HeatStress")
library(weathermetrics)
library(wbgt)  #devtools::install_github("mdljts/wbgt")
library(easyNCDF)
library(devtools)
library(tabularaster) #devtools::install_github("hypertidy/tabularaster")

# devtools::install_github("hypertidy/silicate")
#.libPaths()
```

## Load Military Installations, Ranges, and Training Areas (MIRTA) Dataset
Accessed from: https://catalog.data.gov/dataset/military-installations-ranges-and-training-areas
Metadata updated date: January 18, 2017
```{r load_shapefile}
#Ref: http://strimas.com/r/tidy-sf/
bases <- st_read("D:/heat/installations_ranges/MIRTA_Boundaries.shp") %>% 
  janitor::clean_names()



# Filter Fort Knox
# convert to `st_geometrty` SpatialPolygons DataFrame
# Identify centroid of shapefile

knox_sfc <-
  bases %>% 
    dplyr::filter(
        str_detect(.$site_name, "Knox")) %>% 
    mutate(centroid = st_centroid(geometry)) %>% 
    dplyr::select(-c("component", "joint_base", "country", "oper_stat"))


# write_rds(knox_sfc, path = "data/knox_sfc.rds")


```


## Extract NLDAS-2

extract variables from NLDAS-2 netCDF files by converting .nc4 to raster and selecting by raster cell position. It includes a function to extract a single file and applies purrr:map2_dfc to map over each file and each defined variable.



```{r extract_variable_names}

#NLDAS files from 19900101 - 20190715

file_list <- list.files(path = "D:/nldas", pattern = "^.*\\.(nc4|NC4|Nc4|Nc4)$",
                        full.names = FALSE) %>% 
  as_tibble() %>% 
  mutate(date = value %>% 
           stringr::str_extract("[1-2][0-9]{7}") %>% lubridate::ymd(),
         hour = value %>% 
           stringr::str_extract("[0-2][0-9][0]{2}") %>% as_factor(),
         path = paste0("D:/nldas/", value)) %>% 
  dplyr::select(value, path, date, hour) %>% 
  filter(date >= "1990-01-01")

file_list %>% tail()

file_list <-
  file_list %>% 
    slice(20158:258901)



nldas_variables <- c("TMP", "SPFH", "PRES", "UGRD", "VGRD", "DSWRF")

```

## Raster: Read ncdf4 files

```{r id_raster_cells}
coordinates_matrix <- st_coordinates(knox_sfc$centroid)

# Open raster from sample NLDAS file

r <- raster(file_list$path[1], varname = "TMP", quick = "TRUE")


# ID NLDAS grid cells corresponding to centroid coordinates

cell <- tabularaster::cellnumbers(r, coordinates_matrix)


# Define file paths 

nldas_path <- "D:/nldas/"

cells <- cell$cell_

sites <- knox_sfc$site_name

cell_key <- cbind(sites, cells)

output_path <- "D:/nldas_knox/"

file_names <-
  file_list$value


```


```{r extract_function_map}

# multiple variables

  
extract_single_file <- function(ncdf_single_file, nldas_var) {  
  hourly_df <-   
  ncdf_single_file %>% 
      file.path(nldas_path, .) %>% 
        raster::brick(varname = nldas_var, quick = TRUE) %>%
        raster::extract(., cells, df = FALSE) %>% 
        magrittr::set_colnames(nldas_var) %>%
    as_tibble()
}

extract_single_file <- compiler::cmpfun(extract_single_file)



 





# Execute map over files (Jan 1990-July 2019)



ptm <- proc.time()

for (i in seq_along(file_names)) {
map2_dfc(.x = file_names[[i]], .y = nldas_variables, .f = extract_single_file) %>% 
write_rds(., path = paste0(output_path,
                           paste0(
    file_names[[i]] %>%  stringr::str_extract("[1-2][0-9]{7}"),
    "_",
    file_names[[i]] %>% stringr::str_extract("\\.[0-2][0-9][0]{2}") %>% str_sub(start = 2L)),
    ".rds"), 
    compress = "none")
}

proc.time() - ptm


#  user   system  elapsed 
# 47201.04  8612.41 79413.64 

79413.64/(60*60) # 22+ hours




# July 2019 - Dec 2019

nldas_path <- "D:/nldas_end2019/"

extract_single_file <- function(ncdf_single_file, nldas_var) {  
  hourly_df <-   
  ncdf_single_file %>% 
      file.path(nldas_path, .) %>% 
        raster::brick(varname = nldas_var, quick = TRUE) %>%
        raster::extract(., cells, df = FALSE) %>% 
        magrittr::set_colnames(nldas_var) %>%
    as_tibble()
}


file_list <- list.files(path = "D:/nldas_end2019", pattern = "^.*\\.(nc4|NC4|Nc4|Nc4)$",
                        full.names = FALSE) %>% 
  as_tibble() %>% 
  mutate(date = value %>% 
           stringr::str_extract("[1-2][0-9]{7}") %>% lubridate::ymd(),
         hour = value %>% 
           stringr::str_extract("[0-2][0-9][0]{2}") %>% as_factor(),
         path = paste0("D:/nldas_end2019/", value)) %>% 
  dplyr::select(value, path, date, hour) 

file_names <-
  file_list$value




for (i in seq_along(file_names)) {
map2_dfc(.x = file_names[[i]], .y = nldas_variables, .f = extract_single_file) %>% 
write_rds(., path = paste0(output_path,
                           paste0(
    file_names[[i]] %>%  stringr::str_extract("[1-2][0-9]{7}"),
    "_",
    file_names[[i]] %>% stringr::str_extract("\\.[0-2][0-9][0]{2}") %>% str_sub(start = 2L)),
    ".rds"), 
    compress = "none")
}








ncdump::NetCDF("D:/nldas/NLDAS_FORA0125_H.A20090510.2000.002.grb.SUB.nc4")
```


## .rds objects to List


# .rds object list

```{r extract_variable_names}


file_list <- list.files(path = "D:/nldas_knox", pattern = "^.*\\.rds",
                        full.names = TRUE) %>% 
  as_tibble()


nldas_list <- list.files(path = "D:/nldas_knox", pattern = "^.*\\.rds",
                        full.names = TRUE) %>%  
  lapply(., read_rds)


#nldas_list <-
 # list.files(path = "D:/nldas_pens_ports", pattern = ".rds") %>%
  #map(read_rds)


# Set date/time as list element name

date_time_names <- 
  paste0(
      file_list$value %>%  stringr::str_sub(start = -17)
  ) %>% 
  str_sub(end = -5)
        
        
        
#date_time_names %>% as_tibble() %>% n_distinct()
#date_time_names %>% as_tibble() %>% janitor::get_dupes(value)


names(nldas_list) <- date_time_names

# write_rds(nldas_list, path = "D:/output/nldas_list_knox.rds")




```


## Convert NLDAS from list to df

```{r}

nldas_list <-
  read_rds("D:/output/nldas_list_pensa_ports.rds")

knox_bases <- "fort_knox"


# Extract by location from list and create an NLDAS object for each.

knox_df <-
  nldas_list %>% 
    bind_rows(.id = "date_time") %>% 
    mutate(installation = "fort_knox")

 write_rds(knox_df, path = "D:/data/knox_df.rds")



```









```{r plot_raster_cells}

centroid_knox <- knox_sfc$centroid %>%
  as_tibble() %>% 
  dplyr::mutate(site_name = knox_sfc$site_name) %>% 
  st_as_sf()


raster_cell <- 
  xyFromCell(r, cell$cell_) %>%
  as_tibble() %>% 
  mutate(site_name = knox_sfc$site_name) %>% 
  st_as_sf(coords = c("x", "y"))


tm_shape(knox_sfc) +
    tm_borders() +
    tm_fill(col = "blue", alpha = 0.1) +
tm_shape(centroid_knox) +
  tm_dots() +
tm_shape(raster_cell) +
  tm_dots(col = "red") 

```


