---
title: "wbgt_max"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(plotly)
library(lattice)
#remotes::install_github("tylermorganwall/rayshader")
library(rayshader)
library(dlnm)
library(survival)
library(splines)
library(broom)
library(plotly)
library(weathermetrics)
library(viridis)
library(reshape2)
library(magick)
library(av)

```


```{r}

cc_exposure_df <-
  read_rds(file = "data/cc_exposure_df.rds") 

cc_exposure_df <-
  cc_exposure_df %>% 
    mutate("wbgt_mean" = weathermetrics::celsius.to.fahrenheit(wbgt_mean),
           "wbgt_max" = weathermetrics::celsius.to.fahrenheit(wbgt_max))

base_service_df <-
   read_rds(file = "data/base_service_df.rds") 

# Add installation branch of service and climate region

cc_exposure_df <-
  cc_exposure_df %>% 
    left_join(base_service_df %>%
                rename(base_service = service) %>% 
                dplyr::select(installation_name, base_service, region), by = "installation_name") 



daily_indices <- 
  read_rds(file = "data/daily_indices.rds") %>% 
    filter(!installation %in% c("fort_drum", "fort_huachuca", "fort_lewis",
                                "lackland_afb", "fort_carson", "west_point_mil_reservation")) %>% 
    mutate("wbgt_mean" = weathermetrics::celsius.to.fahrenheit(wbgt_mean),
           "wbgt_max" = weathermetrics::celsius.to.fahrenheit(wbgt_max),
            installation = recode(installation,
              "mcb_camp_lejeune" = "camp_lejeune",
              "mcb_camp_pendleton" = "camp_pendleton",
              "fort_benning_ga" = "fort_benning",
              "fort_sam_houston" = "jbsa",
              "mcrd_beaufort_parris_island" = "parris_island",
              "mcb_quantico" = "quantico",
              "twentynine_palms_main_base" = "twentynine_palms")) 
     


daily_indices %>% 
  count(installation) %>% View()

cc_exposure_df %>% 
  count(installation_name) %>% View()

```


# cases at >92 deg F
```{r}

cc_exposure_df %>% 
  filter(wbgt_max >= 92)

# 6,061 cases out of 139,875 gt or equal to 92 max WBGT (~4.3% of cases at or beyond peak)
6061/139875

```




```{r}

# DLNM
## Lags function

lags <- seq(5) # Number of lags

lag_names <- paste("lag", formatC(lags, width = nchar(max(lags)), flag = "0"), 
  sep = "_")

lag_fun <- setNames(paste("dplyr::lag(., ", lags, ")"), lag_names)

```



```{r}

selected_index <- "wbgt_max"


  # create lag matrix

lag_matrix <-
  daily_indices %>% 
    filter(date %in% as.Date("1997-12-15"):as.Date("2019-12-31")) %>% 
      dplyr::select(installation, date, selected_index) %>% 
   group_by(installation) %>% 
   mutate_at(vars(selected_index), funs_(lag_fun)
  )


# join lag matrix to case-crossover dataframe

cc_lag_matrix <-
  cc_exposure_df %>% 
    filter(year %in% 1998:2019) %>% 
    dplyr::select(!selected_index) %>%    # remove to avoid double listing after join
    left_join(lag_matrix,  by = c("installation_name" = "installation", "date" = "date")) 


cc_lag_only <- 
  cc_lag_matrix %>% 
  dplyr::select(selected_index, lag_1:lag_5)


# Define dlnm cross-basis (penalized splines)

index_cb <-
    crossbasis(
      cc_lag_only,    
      lag = 5,    # of lags
      argvar = list(fun = "ns", df = 5),    #  functional form of the dose-response curve
      arglag = list(fun = "ns", df = 4))    #  functional form of the lags

summary(index_cb)

# run model and get prediction for selected_index


index_dlnm <- survival::clogit(case ~ 
                  index_cb +  # lagged, nonlinear term for exposure
                  strata(stratum), 
                  method = "efron",
                  data =  cc_exposure_df) 


pred_dlnm <- crosspred(index_cb, index_dlnm, by = 1, from = 0, to = 110, cen = 55, cumul = TRUE)

summary(pred_dlnm)

## Overall effect RRs

pred_dlnm$allRRfit[c("74", "78", "80", "82", "84", "86", "88")]

bind_cols(names(pred_dlnm$allRRfit), pred_dlnm$allRRfit, pred_dlnm$allRRlow, pred_dlnm$allRRhigh) %>% 
  dplyr::rename(var = 1, rr = 2, ci_low = 3, ci_high = 4) %>% 
  dplyr::filter(var %in% c("74", "78", "80", "82", "84", "86", "88"))



```


## Plot model (ggplot)
```{r}

# As ggplot
  # https://www.rdocumentation.org/packages/season/versions/0.3.8/vignettes/season-vignette.Rmd link assisted with example "Plot of the temperature and death association averaging over all lags"

 
to_plot <- 
  data.frame(index = pred_dlnm$predvar, 
             mean = pred_dlnm$allRRfit,
             lower = pred_dlnm$allRRlow,
             upper = pred_dlnm$allRRhigh)




ggplot(data = to_plot, aes(x = index, y = mean, ymin = lower, ymax = upper)) +
  geom_hline(lty = 2, yintercept = 1) + # horizontal reference line at no change in odds
  geom_ribbon(alpha = 0.2, fill = "cadetblue", color = "cadetblue") +
  geom_line(size = 1.25) +
  xlab('Max WBGT (°F)') +
  ylab('Odds Ratio') +
  xlim(55, NA) +
  theme_bw() +
  ggtitle("Daily max WBGT and HSI association \ncumulative over 0-5 days lag") +
  labs(caption = "ORs relative to 55°F max WBGT") +
  theme(plot.caption = element_text(hjust = 0)) 


# "Base R" plots by lag "slices"  

plot(pred_dlnm, "slices",
     lag = 0,
     ylim = c(0, 25),
     xlim = c(55, 110),
     lwd = 4,
     col = "red",
     main = "Exposure-Response Effects by Lag Day  \n  1998-2019", 
     xlab = "Max WBGT (°F)", 
     ylab = "HSI Rate Ratio")


lines(pred_dlnm, "slices",
     lag = 1,
     lwd = 4,
     col = "blue"
)

lines(pred_dlnm, "slices",
     lag = 2,
     lwd = 4,
     col = "green"
)


lines(pred_dlnm, "slices",
     lag = 3,
     lwd = 4,
     col = "orange")

legend("topleft", legend = c("Lag 0", "Lag 1", "Lag 2", "Lag 3"),
       col = c("red", "blue", "green", "orange"), lty = 1, cex = 1)


#3D Plot prep

plot(pred_dlnm, 
     xlab = paste(selected_index), zlab = "\nRR", ylab = "\nLag", 
     theta = 40, phi = 30, lphi = 30,
     main = "1998-2019")


# https://rdrr.io/cran/dlnm/src/R/seqlag.R
seqlag <- function(lag,by = 1) seq(from = lag[1],to = lag[2],by = by)



to_plot <- 
  data.frame(index = pred_dlnm$predvar, 
             mean = pred_dlnm$allRRfit,
             lower = pred_dlnm$allRRlow,
             upper = pred_dlnm$allRRhigh)


to_3d <- list(x = matrix(pred_dlnm$predvar), 
              y = matrix(seqlag(pred_dlnm$lag, pred_dlnm$bylag)), 
              z = matrix(unlist(pred_dlnm$matfit), ncol = 6, byrow = TRUE))


x <- as_vector(pred_dlnm$predvar)
y <- as.vector(seqlag(pred_dlnm$lag, pred_dlnm$bylag))
z <- pred_dlnm$matRRfit

df_3d <-  
  z %>% 
    melt() %>% 
    as_tibble() %>% 
    rename(
      "Max WBGT" = Var1,
      "Lag" = Var2,
      "OR" = value
    ) %>% 
    mutate(Lag = as.numeric(str_remove(Lag, "lag"))) 

df_3d$OR %>% summary()



# 3d plot with rayshader

gg_3d <-
  df_3d %>% 
  filter(`Max WBGT` >= 55) %>% 
  ggplot() +
    geom_raster(aes(x = `Max WBGT`, y = `Lag`, fill = `OR`)) +
    scale_fill_viridis()



plot_gg(gg_3d, multicore = TRUE, width = 5, height = 5, scale = 250)


filename_movie <- "output/max_wbgt_3d.mp4"

render_movie(filename = filename_movie, type = "orbit", 
             frames = 360,  phi = 30, zoom = 0.8, theta = -90,
             title_text = "Max WBGT Odds Ratio")


# 3D print file
#filename_stl = "output/mean_wbgt_3d.stl"
#save_3dprint(filename_stl, rotate = TRUE)



```



## Examine by region
Nest `cc_exposure_df` by region

```{r}

# join lag matrix to case-crossover dataframe
# mutate new list-column for lag only matrix

wbgt_max_nest_region <-
  cc_exposure_df %>%
    filter(year %in% 1998:2019) %>%
    dplyr::select(!selected_index) %>%    # remove to avoid double listing after join
    left_join(lag_matrix,  by = c("installation_name" = "installation", "date" = "date")) %>% 
    group_by(region) %>% 
    nest() %>% 
    rename(cc_lag_matrix = data) %>% 
    mutate(cc_lag_only =
             map(cc_lag_matrix, ~ .x %>% dplyr::select(selected_index, lag_1:lag_5)),
           index_cb = 
             map(cc_lag_only, ~ crossbasis(
                .x,    
                lag = 5,    # of lags
                argvar = list(fun = "ns", df = 5),    #  functional form of the dose-response curve
                arglag = list(fun = "ns", df = 4))                
              ),
           index_dlnm = 
             map2(.x = index_cb, .y = cc_lag_matrix,  ~ survival::clogit(case ~ 
                    .x +  # lagged, nonlinear term for exposure
                    strata(stratum), 
                    method = "efron",
                    data =  .y)),
            pred_dlnm = 
              map2(.x = index_cb, .y = index_dlnm, ~ crosspred(
                .x, .y, by = 1, from = 0, to = 110, cen = 55, cumul = TRUE)))
            

wbgt_max_nest_region



# Plot cumulative lag

to_plot_region <-
  wbgt_max_nest_region %>% 
    mutate(to_plot = 
             map(.x = pred_dlnm, ~ 
                   data.frame(index = .x$predvar, 
                      mean = .x$allRRfit,
                      lower = .x$allRRlow,
                      upper = .x$allRRhigh))) %>% 
    dplyr::select(region, to_plot) %>% 
      unnest(to_plot)



ggplot(data = to_plot_region, aes(x = index, y = mean, ymin = lower, ymax = upper, color = region, fill = region)) +
  geom_hline(lty = 2, yintercept = 1) + # horizontal reference line at no change in odds
  geom_ribbon(alpha = 0.1, colour = NA) +
  geom_line(size = 1.25) +
  xlab('Max WBGT (°F)') +
  ylab('Odds Ratio') +
  xlim(55, NA) +
  theme_bw() +
  ggtitle("Daily max WBGT and HSI association cumulative\nover 0-5 days lag by NOAA NCEI climate region") +
  labs(caption = "ORs relative to 55°F max WBGT") +
  theme(plot.caption = element_text(hjust = 0)) 


```



## Examine by installation primary* branch of service

Note: there is overlap at sites (eg JBSA incl Lackland AFB and Fort Sam Houston)
Nest `cc_exposure_df` by `base_service`

```{r}

# join lag matrix to case-crossover dataframe
# mutate new list-column for lag only matrix

wbgt_max_nest_service <-
  cc_exposure_df %>%
    filter(year %in% 1998:2019) %>%
    dplyr::select(!selected_index) %>%    # remove to avoid double listing after join
    left_join(lag_matrix,  by = c("installation_name" = "installation", "date" = "date")) %>% 
    group_by(base_service) %>% 
    nest() %>% 
    rename(cc_lag_matrix = data) %>% 
    mutate(cc_lag_only =
             map(cc_lag_matrix, ~ .x %>% dplyr::select(selected_index, lag_1:lag_5)),
           index_cb = 
             map(cc_lag_only, ~ crossbasis(
                .x,    
                lag = 5,    # of lags
                argvar = list(fun = "ns", df = 5),    #  functional form of the dose-response curve
                arglag = list(fun = "ns", df = 4))                
              ),
           index_dlnm = 
             map2(.x = index_cb, .y = cc_lag_matrix,  ~ survival::clogit(case ~ 
                    .x +  # lagged, nonlinear term for exposure
                    strata(stratum), 
                    method = "efron",
                    data =  .y)),
            pred_dlnm = 
              map2(.x = index_cb, .y = index_dlnm, ~ crosspred(
                .x, .y, by = 1, from = 0, to = 110, cen = 55, cumul = TRUE)))
            

wbgt_max_nest_service



# Plot cumulative lag

to_plot_region <-
  wbgt_max_nest_service %>% 
    mutate(to_plot = 
             map(.x = pred_dlnm, ~ 
                   data.frame(index = .x$predvar, 
                      mean = .x$allRRfit,
                      lower = .x$allRRlow,
                      upper = .x$allRRhigh))) %>% 
    dplyr::select(base_service, to_plot) %>% 
      unnest(to_plot)



ggplot(data = to_plot_region, aes(x = index, y = mean, ymin = lower, ymax = upper, color = base_service, fill = base_service)) +
  geom_hline(lty = 2, yintercept = 1) + # horizontal reference line at no change in odds
  geom_ribbon(alpha = 0.1, colour = NA) +
  geom_line(size = 1.25) +
  xlab('Max WBGT (°F)') +
  ylab('Odds Ratio') +
  xlim(55, NA) +
  ylim(NA, 200) +
  theme_bw() +
  ggtitle("Daily max WBGT and HSI association cumulative\nover 0-5 days lag by installation primary service branch") +
  labs(caption = "ORs relative to 55°F max WBGT") +
  theme(plot.caption = element_text(hjust = 0)) 


```




## Examine by time in season

1st look: pre vs post 4th of July 
days 0-185 (early season) vs days 186-366 (late season) 

  mutate(`Day of Year` = lubridate::yday(date))
```{r}


# join lag matrix to case-crossover dataframe
# mutate new list-column for lag only matrix

wbgt_max_nest_tis <-
  cc_exposure_df %>%
    filter(year %in% 1998:2019) %>%
    dplyr::select(!selected_index) %>%    # remove to avoid double listing after join
    left_join(lag_matrix,  by = c("installation_name" = "installation", "date" = "date")) %>%
    mutate(`Day of Year` = lubridate::yday(date),
           `Time in season` = case_when(
                 `Day of Year` <= 185 ~ "Early season",
                   `Day of Year` > 185 ~ "Late season"
              )) %>% 
    group_by(`Time in season`) %>% 
    nest() %>% 
    rename(cc_lag_matrix = data) %>% 
    mutate(cc_lag_only =
             map(cc_lag_matrix, ~ .x %>% dplyr::select(selected_index, lag_1:lag_5)),
           index_cb = 
             map(cc_lag_only, ~ crossbasis(
                .x,    
                lag = 5,    # of lags
                argvar = list(fun = "ns", df = 5),    #  functional form of the dose-response curve
                arglag = list(fun = "ns", df = 4))                
              ),
           index_dlnm = 
             map2(.x = index_cb, .y = cc_lag_matrix,  ~ survival::clogit(case ~ 
                    .x +  # lagged, nonlinear term for exposure
                    strata(stratum), 
                    method = "efron",
                    data =  .y)),
            pred_dlnm = 
              map2(.x = index_cb, .y = index_dlnm, ~ crosspred(
                .x, .y, by = 1, from = 0, to = 110, cen = 55, cumul = TRUE)))
            

wbgt_max_nest_tis



# Plot cumulative lag

to_plot_region <-
  wbgt_max_nest_tis %>% 
    mutate(to_plot = 
             map(.x = pred_dlnm, ~ 
                   data.frame(index = .x$predvar, 
                      mean = .x$allRRfit,
                      lower = .x$allRRlow,
                      upper = .x$allRRhigh))) %>% 
    dplyr::select(`Time in season`, to_plot) %>% 
      unnest(to_plot)



ggplot(data = to_plot_region, aes(x = index, y = mean, ymin = lower, ymax = upper, color = `Time in season`, fill = `Time in season`)) +
  geom_hline(lty = 2, yintercept = 1) + # horizontal reference line at no change in odds
  geom_ribbon(alpha = 0.1, colour = NA) +
  geom_line(size = 1.25) +
  xlab('Max WBGT (°F)') +
  ylab('Odds Ratio') +
  xlim(55, NA) +
  ylim(NA, 40) +
  theme_bw() +
  ggtitle("Daily max WBGT and HSI association cumulative\nover 0-5 days lag by time in season") +
  labs(caption = "ORs relative to 55°F max WBGT") +
  theme(plot.caption = element_text(hjust = 0)) 


```



